---
title: "Other outcomes DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LUCAS table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'LASA1B', 'LASA.LASA1B', variables=list('byear','bhart05','bhart06','bcva04','bcva03','bdiabe01','bdiabe02','bdiabe03','bdiabe04','bdiabe04','bmweight','bmwaist','bsubhea1','bmed_hyp','bmvar156','bhart10','bcva02','diabe02','bcva01','badl1a','bmed157','bmed156','bmlength','bmvar152','bhart01','bhart11','bhart07','bhart08','bage','bmvar152'))
LASA1B <- opal.execute(erasmus_opal,'LASA1B')

opal.assign.table.tibble(erasmus_opal, 'LASA1C', 'LASA.LASA1C', variables=list('chbd1','ccva02a',"chart05",'chart05','chart06','ccva04','ccva03','cdiabe01','cdiabe02','cdiabe03','cdiabe04','cmweight','cmwaist','csubhea1','cmed153','cmed155','cmed150','cmed152','csubhea1','cadl1a','cmvar307','cmed152','cmage','cage','ccva01','ccva02b','ccva03j','ccva04j','ccva01','cmed156','cmed157','cadl1a','cadl5a','chart11','chart01','chart10','byear','chart07j','chart08j'))
LASA1C <- opal.execute(erasmus_opal,'LASA1C')

opal.assign.table.tibble(erasmus_opal, 'LASA1D', 'LASA.LASA1D', variables=list('dhbd1','dcva02a','dcva02b','dhart05','dhart06','dcva04','dcva03','ddiabe01','ddiabe02','ddiabe03','ddiabe04','dmed153','dmed155','dmed150','dmed152','dmwaist','dsubhea1','dmed155','dmed152','dcva01','dmed156','dadl1a','dadl5a','dmed157','dmed156','dhart11','dhart01','dhart10','byear',"dhart01","dhart05","dhart06","dhart07j","dhart08j","dhart10","dhart11","dcva01","dcva02a","dcva02b","dcva03j","dcva04j"))
LASA1D <- opal.execute(erasmus_opal,'LASA1D')

opal.assign.table.tibble(erasmus_opal, 'LASA1E', 'LASA.LASA1E', variables=list('ehbd1','ehbd2a','ecva02a','ecva02b','emed155','emed153','emed152','emed150','ehart05','ehart06','ecva04','ecva03','ediabe01','ediabe02','ediabe03','ediabe04','ediabe04','emweight','emwaist','emed156','emed157','esubhea1','emed155','emed152','ecva01','eadl5a','emed157','ehart11','ehart01','ehart10','byear',"ehart01","ehart05","ehart06","ehart07j","ehart08j","ehart10","ehart11","ecva01","ecva02a","ecva02b","ecva03j","ecva04j"))
LASA1E <- opal.execute(erasmus_opal,'LASA1E')

opal.assign.table.tibble(erasmus_opal, 'LASA1F', 'LASA.LASA1F', variables=list('fhbd1','fhbd2a','fcva02a','fcva02b','fhart05','fhart06','fcva04','fcva03','fdiabe01','fdiabe02','fdiabe03','fdiabe04','fdiabe04','fmed153','fmed155','fmweight','fmwaist','fsubhea1','fmed152','fmed150','fcva01','fadl5a','fmed156','fmed157','fhart11','fhart10','fhart01','byear',"fhart01","fhart05","fhart06","fhart07j","fhart08j","fhart10","fhart11","fcva01","fcva02a","fcva02b","fcva03j","fcva04j"))
LASA1F <- opal.execute(erasmus_opal,'LASA1F')

opal.assign.table.tibble(erasmus_opal, 'LASA1G', 'LASA.LASA1G', variables=list('ghbd1','ghbd2a','ghart05','ghart06','gcva04','gcva03','gcva02a','gcva02b','gdiabe01','gdiabe02','gdiabe03','gdiabe04','gdiabe04','gmweight','gmed155','gmed153','gmed152','gmed150','gmwaist','gsubhea1','gmed155','gmed152','gcva01','gmed153','gadl5a','gmed156','gmed157','ghart11','byear',"ghart01","ghart05","ghart06","ghart07j","ghart08j","ghart10","ghart11","gcva01","gcva02a","gcva02b","gcva03j","gcva04j"))
LASA1G <- opal.execute(erasmus_opal,'LASA1G')

opal.assign.table.tibble(erasmus_opal, 'LASA1H', 'LASA.LASA1H', variables=list('HHBD1','HHBD2A','HHART06','HHART05','HCVA02A','HCVA02B','HDIABE01','HDIABE02','HDIABE03','HDIABE04','HMED155','HMED153','HMED150','HMED152','HMED152','HCVA01','hsubhea1','HADL5A','HMED156','HMED157','BHART11','byear',"HHART01","HHART05","HHART06","HHART07J","HHART08J","HHART10","HHART11"))
LASA1H <- opal.execute(erasmus_opal,'LASA1H')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
oth_LASA1_0 <- data.frame(id = LASA1B$id)
oth_LASA1_1 <- data.frame(id = LASA1C$id)
oth_LASA1_2 <- data.frame(id = LASA1D$id)
oth_LASA1_3 <- data.frame(id = LASA1E$id)
oth_LASA1_4 <- data.frame(id = LASA1F$id)
oth_LASA1_5 <- data.frame(id = LASA1G$id)
oth_LASA1_6 <- data.frame(id = LASA1H$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [Diabetes subdomain](#diabetes-subdomain)
6. [BMI subdomain](#bmi-subdomain)
7. [General perception of health subdomain](#general-perception-of-health-subdomain)
8. [Disability subdomain](#disability-subdomain)

# Hypertension subdomain

### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_0  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  impossible  
**Harmonization comment**:   Study-specific variable is use of antiypertensives (bmed_hyp).  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_1  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$dis_hbp_ever_1 <- recode(as.integer(LASA1C$chbd1), '1'=0L,'2'=1L, .default=NA_integer_)
``` 
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_0  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension  


**Harmonization status**: impossible        
**Harmonization comment**:  Study-specific variable is current use of medication for hypertension (bmed_hyp= use of antihypertensives).  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension  
**Variable name**:  dis_hbp_med_1  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**: impossible  
**Harmonization comment**:  study-specific variables chbd2a = Hypertension: taking medication and cmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_2  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables dhbd2a = Hypertension: taking medication and dmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_3    
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables ehbd2a = Hypertension: taking medication and emed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_4  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables fhbd2a = Hypertension: taking medication and fmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_5  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables ghbd2a = Hypertension: taking medication and gmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.    
**R script**:  
```{r, echo=TRUE}

```  
# Angina subdomain

### **Variable label**: Lifetime occurrence of angina  
**Variable name**:  dis_angina_ever_0  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_1  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

``` 
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_2  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_3  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_4  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```

# Myocardial infarction subdomain

### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_0  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#Merging the raw tables LASA1B-LASA1H
MyMerge <- function(x,y){
  merge(x,y, by= c("id","byear"),all=TRUE)
}
med_table_lasa1 <- Reduce(MyMerge, list(LASA1B,LASA1C,LASA1D,LASA1E,LASA1F,LASA1G,LASA1H))
#Harmonization scripts to create "ever had mi"
med_table_lasa1$dis_mi_ever_0 <- ifelse(as.integer(med_table_lasa1$bhart05)==0 | (as.integer(med_table_lasa1$bhart05)==-2 & as.integer(med_table_lasa1$bhart01)== 0),0L, ifelse(as.integer(med_table_lasa1$bhart05)==1,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_0<-merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_mi_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_1  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**: 	Ever had myocardial infraction was collected at baseline (bhart05). Ever had myocardial infarction was created using "myocardial infarction since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever had mi"
med_table_lasa1$dis_mi_ever_1  <- ifelse(med_table_lasa1$dis_mi_ever_0==1 | (med_table_lasa1$dis_mi_ever_0==0 & as.integer(med_table_lasa1$chart05)==2),1L, ifelse(as.integer(med_table_lasa1$chart01)==0 | (med_table_lasa1$dis_mi_ever_0==0 & (as.integer(med_table_lasa1$chart01)== 2 | as.integer(med_table_lasa1$chart01)== 3) & as.integer(med_table_lasa1$chart05)==1),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_1<-merge(oth_LASA1_1,med_table_lasa1[,c("id","dis_mi_ever_1")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_2  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**: 	Ever had myocardial infraction was collected at baseline (bhart05). Ever had myocardial infarction was created using "myocardial infarction since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.    
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever had mi"
med_table_lasa1$dis_mi_ever_2  <- ifelse(med_table_lasa1$dis_mi_ever_1==1 | (med_table_lasa1$dis_mi_ever_1==0 & as.integer(med_table_lasa1$dhart05)==2),1L, ifelse(as.integer(med_table_lasa1$dhart01)==0 | (med_table_lasa1$dis_mi_ever_1==0 & (as.integer(med_table_lasa1$dhart01)== 2 | as.integer(med_table_lasa1$dhart01)== 3) & as.integer(med_table_lasa1$dhart05)==1),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_2<-merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_mi_ever_2")],by="id",all.x=TRUE)

```  

### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_0  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete    
**Harmonization comment**:  Age at first myocardial infraction was collected at baseline (bhart07 & bhart 08). Age at first myocardial infarction was created using "myocardial infarction since last interview", "year of mi if one mi since last interview" and "year of first mi if more than one mi since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age had first mi"
med_table_lasa1$dis_mi_age_0 <- ifelse(med_table_lasa1$bhart05==1 & med_table_lasa1$bhart06==1, ifelse(med_table_lasa1$bhart07>=0 & med_table_lasa1$bhart07< med_table_lasa1$bage,med_table_lasa1$bhart07,NA), ifelse(med_table_lasa1$bhart05==1 & med_table_lasa1$bhart06==2, ifelse(med_table_lasa1$bhart08>=0 & med_table_lasa1$bhart08 < med_table_lasa1$bage, med_table_lasa1$bhart08,NA),NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_0 <- merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_mi_age_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_1  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:  Age at first myocardial infraction was collected at baseline (bhart07 & bhart 08). Age at first myocardial infarction was created using "myocardial infarction since last interview", "year of mi if one mi since last interview" and "year of first mi if more than one mi since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age had first mi"
med_table_lasa1$chart07j_yr <- as.integer(ifelse(med_table_lasa1$chart07j>0,paste(19, med_table_lasa1$chart07j, sep = ""),med_table_lasa1$chart07j))
med_table_lasa1$chart08j_yr <- as.integer(ifelse(med_table_lasa1$chart08j>0,paste(19, med_table_lasa1$chart08j, sep = ""),med_table_lasa1$chart08j))

med_table_lasa1$dis_mi_age_1 <- ifelse(med_table_lasa1$dis_mi_ever_0==1, med_table_lasa1$dis_mi_age_0, ifelse(med_table_lasa1$dis_mi_ever_0==0 & med_table_lasa1$chart05==2 & med_table_lasa1$chart06==1, ifelse(med_table_lasa1$chart07j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$chart07j_yr > med_table_lasa1$byear, med_table_lasa1$chart07j_yr - med_table_lasa1$byear,NA), ifelse(med_table_lasa1$dis_mi_ever_0==0 & med_table_lasa1$chart05==2 & med_table_lasa1$chart06==2, ifelse(med_table_lasa1$chart08j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$chart08j_yr > med_table_lasa1$byear, med_table_lasa1$chart08j_yr - med_table_lasa1$byear,NA),NA)))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_1<- merge(oth_LASA1_1,med_table_lasa1[,c("id","dis_mi_age_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_2  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete      
**Harmonization comment**:  Age at first myocardial infraction was collected at baseline (bhart07 & bhart 08). Age at first myocardial infarction was created using "myocardial infarction since last interview", "year of mi if one mi since last interview" and "year of first mi if more than one mi since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age had first mi"
med_table_lasa1$dhart07j_yr <- as.integer(ifelse(med_table_lasa1$dhart07j>0,paste(19, med_table_lasa1$dhart07j, sep = ""),med_table_lasa1$dhart07j))
med_table_lasa1$dhart08j_yr <- as.integer(ifelse(med_table_lasa1$dhart08j>0,paste(19, med_table_lasa1$dhart08j, sep = ""),med_table_lasa1$dhart08j))

med_table_lasa1$dis_mi_age_2 <- ifelse(med_table_lasa1$dis_mi_ever_1==1, med_table_lasa1$dis_mi_age_1, ifelse(med_table_lasa1$dis_mi_ever_1==0 & med_table_lasa1$dhart05==2 & med_table_lasa1$dhart06==1, ifelse(med_table_lasa1$dhart07j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$dhart07j_yr > med_table_lasa1$byear, med_table_lasa1$dhart07j_yr - med_table_lasa1$byear,NA), ifelse(med_table_lasa1$dis_mi_ever_1==0 & med_table_lasa1$dhart05==2 & med_table_lasa1$dhart06==2, ifelse(med_table_lasa1$dhart08j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$dhart08j_yr > med_table_lasa1$byear, med_table_lasa1$dhart08j_yr - med_table_lasa1$byear,NA),NA)))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_2<- merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_mi_age_2")],by="id",all.x=TRUE)
```  
# Stroke subdomain

### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_0  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "stroke ever"
med_table_lasa1$dis_stroke_ever_0 <- recode(as.integer(med_table_lasa1$bcva01),'0'=0L,'1'=1L,.default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_0<-merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_stroke_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_1  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "stroke ever"
med_table_lasa1$dis_stroke_ever_1 <- ifelse(med_table_lasa1$dis_stroke_ever_0==1 | (med_table_lasa1$dis_stroke_ever_0==0 & med_table_lasa1$ccva02a==2),1L, ifelse(med_table_lasa1$dis_stroke_ever_0==0 & (med_table_lasa1$ccva02a==1 | med_table_lasa1$ccva02a==-2),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_1<- merge(oth_LASA1_1, med_table_lasa1[,c("id","dis_stroke_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_2  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "stroke ever"
med_table_lasa1$dis_stroke_ever_2 <- ifelse(med_table_lasa1$dis_stroke_ever_1==1 | (med_table_lasa1$dis_stroke_ever_1==0 & med_table_lasa1$dcva02a==2),1L, ifelse(med_table_lasa1$dis_stroke_ever_1==0 & (med_table_lasa1$dcva02a==1 | med_table_lasa1$dcva02a==-2),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_2<- merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_stroke_ever_2")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_0  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age frist sroke"
med_table_lasa1$dis_stroke_age_0 <-ifelse(med_table_lasa1$bcva01==1 & med_table_lasa1$bcva02==1, ifelse(med_table_lasa1$bcva03>=0 & med_table_lasa1$bcva03 < med_table_lasa1$bage, med_table_lasa1$bcva03,NA), ifelse(med_table_lasa1$bcva01==1 & med_table_lasa1$bcva02==2, ifelse(med_table_lasa1$bcva04>=0 & med_table_lasa1$bcva04 < med_table_lasa1$bage, med_table_lasa1$bcva04,NA),NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_0<- merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_stroke_age_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_1  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:  Age at first stroke was collected at baseline (bcva03 & bcva04). Age at first stroke was created using "sroke since last interview", "year of stroke if one stroke since last interview" and "year of first stroke if more than one stroke since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.    
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age frist sroke"
med_table_lasa1$ccva03j_yr <- as.integer(ifelse(med_table_lasa1$ccva03j>0,paste(19, med_table_lasa1$ccva03j, sep = ""),med_table_lasa1$ccva03j))
med_table_lasa1$ccva04j_yr <- as.integer(ifelse(med_table_lasa1$ccva04j>0,paste(19, med_table_lasa1$ccva04j, sep = ""),med_table_lasa1$ccva04j))

med_table_lasa1$dis_stroke_age_1 <- ifelse(med_table_lasa1$dis_stroke_ever_0==1, med_table_lasa1$dis_stroke_age_0, ifelse(med_table_lasa1$dis_stroke_age_0==0 & med_table_lasa1$ccva02a==2 & med_table_lasa1$ccva02b==1, ifelse(med_table_lasa1$ccva03j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$ccva03j_yr > med_table_lasa1$byear, med_table_lasa1$ccva03j_yr - med_table_lasa1$byear,NA), ifelse(med_table_lasa1$dis_stroke_ever_0==0 & med_table_lasa1$ccva02a==2 & med_table_lasa1$ccva02b==2, ifelse(med_table_lasa1$ccva04j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$ccva04j_yr > med_table_lasa1$byear, med_table_lasa1$ccva04j_yr - med_table_lasa1$byear,NA),NA)))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_1<- merge(oth_LASA1_1,med_table_lasa1[,c("id","dis_stroke_age_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_2  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**: Age at first stroke was collected at baseline (bcva03 & bcva04). Age at first stroke was created using "sroke since last interview", "year of stroke if one stroke since last interview" and "year of first stroke if more than one stroke since last interview" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.     
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "age frist sroke"
med_table_lasa1$dcva03j_yr <- as.integer(ifelse(med_table_lasa1$dcva03j>0,paste(19, med_table_lasa1$dcva03j, sep = ""),med_table_lasa1$dcva03j))
med_table_lasa1$dcva04j_yr <- as.integer(ifelse(med_table_lasa1$dcva04j>0,paste(19, med_table_lasa1$dcva04j, sep = ""),med_table_lasa1$dcva04j))

med_table_lasa1$dis_stroke_age_2 <- ifelse(med_table_lasa1$dis_stroke_ever_1==1, med_table_lasa1$dis_stroke_age_1, ifelse(med_table_lasa1$dis_stroke_ever_1==0 & med_table_lasa1$dcva02a==2 & med_table_lasa1$dcva02b==1, ifelse(med_table_lasa1$dcva03j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$dcva03j_yr > med_table_lasa1$byear, med_table_lasa1$dcva03j_yr - med_table_lasa1$byear,NA), ifelse(med_table_lasa1$dis_stroke_ever_1==0 & med_table_lasa1$dcva02a==2 & med_table_lasa1$dcva02b==2, ifelse(med_table_lasa1$dcva04j_yr>=0 & med_table_lasa1$byear>=0 & med_table_lasa1$dcva04j_yr > med_table_lasa1$byear, med_table_lasa1$dcva04j_yr - med_table_lasa1$byear,NA),NA)))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA1_2<-merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_stroke_age_2")],by="id",all.x=TRUE)
```  


# Diabetes subdomain  

### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar  
**Variable name**: dis_diab_ever_0  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  
**R script**:  
```{r, echo=TRUE}  
med_table_lasa1$dis_diab_ever_0<- recode(as.integer(LASA1B$bdiabe01),'0'=0L,'1'=1L, .default=NA_integer_)

oth_LASA1_0<-merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_diab_ever_0")],by="id",all.x = TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: dis_diab_ever_1  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_1$dis_diab_ever_1 <- recode(as.integer(LASA1C$cdiabe01), '0'=0L, '1'=1L, '2'=1L, '3'=1L, .default=NA_integer_)
med_table_lasa1$dis_diab_ever_1<- ifelse(med_table_lasa1$dis_diab_ever_0==0 & as.integer(med_table_lasa1$cdiabe01)==0,0L, ifelse(med_table_lasa1$dis_diab_ever_0==1| as.integer(med_table_lasa1$cdiabe01)==1 | as.integer(med_table_lasa1$cdiabe01)==2 | as.integer(med_table_lasa1$cdiabe01)==3,1L,NA))

oth_LASA1_1<- merge(oth_LASA1_1,med_table_lasa1[,c("id","dis_diab_ever_1")],by="id", all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_2  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_2$dis_diab_ever_2 <- recode(as.integer(LASA1D$ddiabe01), '0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
med_table_lasa1$dis_diab_ever_2<- ifelse(med_table_lasa1$dis_diab_ever_1==0 & as.integer(med_table_lasa1$ddiabe01)==0,0L, ifelse(med_table_lasa1$dis_diab_ever_1==1| as.integer(med_table_lasa1$ddiabe01)==1 | as.integer(med_table_lasa1$ddiabe01)==2 | as.integer(med_table_lasa1$ddiabe01)==3,1L,NA))

oth_LASA1_2<- merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_diab_ever_2")],by="id", all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: dis_diab_ever_3  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_3$dis_diab_ever_3 <- recode(as.integer(LASA1E$ediabe01),'0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
med_table_lasa1$dis_diab_ever_3<- ifelse(med_table_lasa1$dis_diab_ever_2==0 & as.integer(med_table_lasa1$ediabe01)==0,0L, ifelse(med_table_lasa1$dis_diab_ever_2==1| as.integer(med_table_lasa1$ediabe01)==1 | as.integer(med_table_lasa1$ediabe01)==2 | as.integer(med_table_lasa1$ediabe01)==3,1L,NA))

oth_LASA1_3<- merge(oth_LASA1_3,med_table_lasa1[,c("id","dis_diab_ever_3")],by="id", all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_4  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_4$dis_diab_ever_4 <- recode(as.integer(LASA1F$fdiabe01),'0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
med_table_lasa1$dis_diab_ever_4<- ifelse(med_table_lasa1$dis_diab_ever_3==0 & as.integer(med_table_lasa1$fdiabe01)==0,0L, ifelse(med_table_lasa1$dis_diab_ever_3==1| as.integer(med_table_lasa1$fdiabe01)==1 | as.integer(med_table_lasa1$fdiabe01)==2 | as.integer(med_table_lasa1$fdiabe01)==3,1L,NA))

oth_LASA1_4<- merge(oth_LASA1_4,med_table_lasa1[,c("id","dis_diab_ever_4")],by="id", all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_5  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_5$dis_diab_ever_5 <- recode(as.integer(LASA1G$gdiabe01),'0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
med_table_lasa1$dis_diab_ever_5<- ifelse(med_table_lasa1$dis_diab_ever_4==0 & as.integer(med_table_lasa1$gdiabe01)==0,0L, ifelse(med_table_lasa1$dis_diab_ever_4==1| as.integer(med_table_lasa1$gdiabe01)==1 | as.integer(med_table_lasa1$gdiabe01)==2 | as.integer(med_table_lasa1$gdiabe01)==3,1L,NA))

oth_LASA1_5<- merge(oth_LASA1_5,med_table_lasa1[,c("id","dis_diab_ever_5")],by="id", all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_0    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}  
med_table_lasa1$dis_diab_age_0 <- ifelse(as.integer(med_table_lasa1$bdiabe02)<0,NA,as.integer(med_table_lasa1$bdiabe02))

oth_LASA1_0<- merge(oth_LASA1_0,med_table_lasa1[,c("id","dis_diab_age_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_1    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  Age at diabetes was collected for respondents who did not have diabetes in previous waves. Age at diabetes was created using "age at diabetes" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_1$dis_diab_age_1 <- ifelse(as.integer(LASA1C$cdiabe02)<0,NA,as.integer(LASA1C$cdiabe02))
med_table_lasa1$dis_diab_age_1<- ifelse(!is.na(med_table_lasa1$dis_diab_age_0), med_table_lasa1$dis_diab_age_0, ifelse(med_table_lasa1$cdiabe02>=0, med_table_lasa1$cdiabe02,NA))

oth_LASA1_1<-merge(oth_LASA1_1,med_table_lasa1[,c("id","dis_diab_age_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_2    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  Age at diabetes was collected for respondents who did not have diabetes in previous waves. Age at diabetes was created using "age at diabetes" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   question    
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_2$dis_diab_age_2 <- ifelse(as.integer(LASA1D$ddiabe02)<0,NA,as.integer(LASA1D$ddiabe02))
med_table_lasa1$dis_diab_age_2<- ifelse(!is.na(med_table_lasa1$dis_diab_age_1), med_table_lasa1$dis_diab_age_1, ifelse(med_table_lasa1$ddiabe02>=0, med_table_lasa1$ddiabe02,NA))

oth_LASA1_2<-merge(oth_LASA1_2,med_table_lasa1[,c("id","dis_diab_age_2")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_3    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**: Age at diabetes was collected for respondents who did not have diabetes in previous waves. Age at diabetes was created using "age at diabetes" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   question   
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_3$dis_diab_age_3 <- ifelse(as.integer(LASA1E$ediabe02)<0,NA,as.integer(LASA1E$ediabe02))
med_table_lasa1$dis_diab_age_3<- ifelse(!is.na(med_table_lasa1$dis_diab_age_2), med_table_lasa1$dis_diab_age_2, ifelse(med_table_lasa1$ediabe02>=0, med_table_lasa1$ediabe02,NA))

oth_LASA1_3<-merge(oth_LASA1_3,med_table_lasa1[,c("id","dis_diab_age_3")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_4    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  Age at diabetes was collected for respondents who did not have diabetes in previous waves. Age at diabetes was created using "age at diabetes" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_4$dis_diab_age_4 <- ifelse(as.integer(LASA1F$fdiabe02)<0,NA,as.integer(LASA1F$fdiabe02))
med_table_lasa1$dis_diab_age_4<- ifelse(!is.na(med_table_lasa1$dis_diab_age_3), med_table_lasa1$dis_diab_age_3, ifelse(med_table_lasa1$fdiabe02>=0, med_table_lasa1$fdiabe02,NA))

oth_LASA1_4<-merge(oth_LASA1_4,med_table_lasa1[,c("id","dis_diab_age_4")],by="id",all.x=TRUE)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_5    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  Age at diabetes was collected for respondents who did not have diabetes in previous waves. Age at diabetes was created using "age at diabetes" of previous and current waves. To create this variable, all LASA1 data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   question  
**R script**:  
```{r, echo=TRUE}  
#oth_LASA1_5$dis_diab_age_5 <- ifelse(as.integer(LASA1G$gdiabe02)<0 ,NA,as.integer(LASA1G$gdiabe02))
med_table_lasa1$dis_diab_age_5<- ifelse(!is.na(med_table_lasa1$dis_diab_age_4), med_table_lasa1$dis_diab_age_4, ifelse(med_table_lasa1$gdiabe02>=0, med_table_lasa1$gdiabe02,NA))

oth_LASA1_5<-merge(oth_LASA1_5,med_table_lasa1[,c("id","dis_diab_age_5")],by="id",all.x=TRUE)
```  

### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_0  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_0$dis_diab_tx_0<- ifelse((as.integer(LASA1B$bdiabe03)==0 & as.integer(LASA1B$bdiabe04)==0) | (as.integer(LASA1B$bdiabe01)==0 & as.integer(LASA1B$bdiabe03)==-2) & (as.integer(LASA1B$bdiabe01)==0 & as.integer(LASA1B$bdiabe04)==-2),0L, ifelse(as.integer(LASA1B$bdiabe03)==1 | as.integer(LASA1B$bdiabe03)==2 | as.integer(LASA1B$bdiabe04)==1 | as.integer(LASA1B$bdiabe04)==2,1L,NA))
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_1  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_1$dis_diab_tx_1<- ifelse(as.integer(LASA1C$cdiabe03)==1 & as.integer(LASA1C$cdiabe04)==1,0L,
                             ifelse(as.integer(LASA1C$cdiabe03)==2 | as.integer(LASA1C$cdiabe03)==3 |
                                    as.integer(LASA1C$cdiabe04)==2 | as.integer(LASA1C$cdiabe04)==3,1L,NA))
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_2  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_2$dis_diab_tx_2<- ifelse(as.integer(LASA1D$ddiabe03)==1 & as.integer(LASA1D$ddiabe04)==1,0L,
                             ifelse(as.integer(LASA1D$ddiabe03)==2 | as.integer(LASA1D$ddiabe03)==3 |
                                    as.integer(LASA1D$ddiabe04)==2 | as.integer(LASA1D$ddiabe04)==3,1L,NA))
```   
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_3  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_3$dis_diab_tx_3<- ifelse(as.integer(LASA1E$ediabe03)==1 & as.integer(LASA1E$ediabe04)==1,0L,
                             ifelse(as.integer(LASA1E$ediabe03)==2 | as.integer(LASA1E$ediabe03)==3 |
                                    as.integer(LASA1E$ediabe04)==2 | as.integer(LASA1E$ediabe04)==3,1L,NA))
```   
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_4  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_4$dis_diab_tx_4<- ifelse(as.integer(LASA1F$fdiabe03)==1 & as.integer(LASA1F$fdiabe04)==1,0L,
                             ifelse(as.integer(LASA1F$fdiabe03)==2 | as.integer(LASA1F$fdiabe03)==3 |
                                    as.integer(LASA1F$fdiabe04)==2 | as.integer(LASA1F$fdiabe04)==3,1L,NA))
```    
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_5  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA1_5$dis_diab_tx_5<- ifelse(as.integer(LASA1G$gdiabe03)==1 & as.integer(LASA1G$gdiabe04)==1,0L,
                             ifelse(as.integer(LASA1G$gdiabe03)==2 | as.integer(LASA1G$gdiabe03)==3 |
                                    as.integer(LASA1G$gdiabe04)==2 | as.integer(LASA1G$gdiabe04)==3,1L,NA))
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_0  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  Categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question  '1'=0L,
**R script**:
```{r, echo=TRUE}
oth_LASA1_0$dis_diab_ins_0 <- recode(as.integer(LASA1B$bdiabe03),'0'=0L,'1'=1L,'2'=0L, .default=NA_integer_)
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_1  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  Categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question  
**R script**:
```{r, echo=TRUE}
oth_LASA1_1$dis_diab_ins_1 <- recode(as.integer(LASA1C$cdiabe03),'1'=0L,'2'=1L,'3'=0L, .default=NA_integer_)
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_2  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  Categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question   
**R script**:
```{r, echo=TRUE}
oth_LASA1_2$dis_diab_ins_2 <- recode(as.integer(LASA1D$ddiabe03),'1'=0L,'2'=1L,'3'=0L, .default=NA_integer_)
```  
# BMI subdomain

### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_0  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_weight_ms_0 <- ifelse(as.numeric(LASA1B$bmweight)< 0, NA, as.numeric(LASA1B$bmweight))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_1  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_weight_ms_1 <- ifelse(as.numeric(LASA1C$cmed153)< 0, NA, as.numeric(LASA1C$cmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_2  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_weight_ms_2 <- ifelse(as.numeric(LASA1D$dmed153)< 0, NA, as.numeric(LASA1D$dmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_3  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_weight_ms_3 <- ifelse(as.numeric(LASA1E$emed153)< 0, NA, as.numeric(LASA1E$emed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_4  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_weight_ms_4 <- ifelse(as.numeric(LASA1F$fmed153)< 0, NA, as.numeric(LASA1F$fmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_5  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_weight_ms_5 <- ifelse(as.numeric(LASA1G$gmed153)< 0, NA, as.numeric(LASA1G$gmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_6  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_weight_ms_6 <- ifelse(as.numeric(LASA1H$HMED153)< 0, NA, as.numeric(LASA1H$HMED153))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_0    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_weight_sr_0 <- ifelse(as.numeric(LASA1B$bmvar156)< 0, NA, as.numeric(LASA1B$bmvar156))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_1    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_weight_sr_1 <- ifelse(as.numeric(LASA1C$cmed155)< 0, NA, as.numeric(LASA1C$cmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_2    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_weight_sr_2 <- ifelse(as.numeric(LASA1D$dmed155)< 0, NA, as.numeric(LASA1D$dmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_3    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_weight_sr_3 <- ifelse(as.numeric(LASA1E$emed155)< 0, NA, as.numeric(LASA1E$emed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_4    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_weight_sr_4 <- ifelse(as.numeric(LASA1F$fmed155)< 0, NA, as.numeric(LASA1F$fmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_5    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_weight_sr_5 <- ifelse(as.numeric(LASA1G$gmed155)< 0, NA, as.numeric(LASA1G$gmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_6    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_weight_sr_6 <- ifelse(as.numeric(LASA1H$HMED155)< 0, NA, as.numeric(LASA1H$HMED155))
```  
### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_0      
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_weight_all_0 <- ifelse(as.numeric(LASA1B$bmweight)< 0, NA, as.numeric(LASA1B$bmweight))
```  

### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_1    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.     
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_weight_all_1 <- ifelse(as.numeric(LASA1C$cmed153)< 0, NA, as.numeric(LASA1C$cmed153))
```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_2    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.      
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_weight_all_2 <- ifelse(as.numeric(LASA1D$dmed153)< 0, NA, as.numeric(LASA1D$dmed153))
```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_3     
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.   
**Value type**: decimal   
**Variable unit**: kg    
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_weight_all_3 <- ifelse(as.numeric(LASA1E$emed153)< 0, NA, as.numeric(LASA1E$emed153))
```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_4    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.    
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_weight_all_4 <- ifelse(as.numeric(LASA1F$fmed153)< 0, NA, as.numeric(LASA1F$fmed153))
```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_5    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.      
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_weight_all_5 <- ifelse(as.numeric(LASA1G$gmed153)< 0, NA, as.numeric(LASA1G$gmed153))
```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_6    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_weight_all_6 <- ifelse(as.numeric(LASA1H$HMED153)< 0, NA, as.numeric(LASA1H$HMED153))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_0  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_height_ms_0 <- ifelse(as.numeric(LASA1B$bmlength)< 0, NA, as.numeric(LASA1B$bmlength))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_1  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_height_ms_1 <- ifelse(as.numeric(LASA1C$cmed150)< 0, NA, as.numeric(LASA1C$cmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_2  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_height_ms_2 <- ifelse(as.numeric(LASA1D$dmed150)< 0, NA, as.numeric(LASA1D$dmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_3  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm    
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_height_ms_3 <- ifelse(as.numeric(LASA1E$emed150)< 0, NA, as.numeric(LASA1E$emed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_4  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_height_ms_4 <- ifelse(as.numeric(LASA1F$fmed150)< 0, NA, as.numeric(LASA1F$fmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_5  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_height_ms_5 <- ifelse(as.numeric(LASA1G$gmed150)< 0, NA, as.numeric(LASA1G$gmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_6  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_height_ms_6 <- ifelse(as.numeric(LASA1H$HMED150)< 0, NA, as.numeric(LASA1H$HMED150))
```  

### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_0  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:  24 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_height_sr_0 <- ifelse(as.numeric(LASA1B$bmvar152)< 0 | as.numeric(LASA1B$bmvar152)==999, NA, as.numeric(LASA1B$bmvar152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_1  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   13 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_height_sr_1 <- ifelse(as.numeric(LASA1C$cmed152)< 0, NA, as.numeric(LASA1C$cmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_2  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:  17 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_height_sr_2 <- ifelse(as.numeric(LASA1D$dmed152)< 0, NA, as.numeric(LASA1D$dmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_3  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   13 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_height_sr_3 <- ifelse(as.numeric(LASA1E$emed152)< 0, NA, as.numeric(LASA1E$emed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_4  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:    13 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_height_sr_4 <- ifelse(as.numeric(LASA1F$fmed152)< 0, NA, as.numeric(LASA1F$fmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_5  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   8 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_height_sr_5 <- ifelse(as.numeric(LASA1G$gmed152)< 0, NA, as.numeric(LASA1G$gmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_6  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   5 participants have values for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_height_sr_6 <- ifelse(as.numeric(LASA1H$HMED152)< 0, NA, as.numeric(LASA1H$HMED152))
```  

### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_0    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.     
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_height_all_0 <- ifelse(as.numeric(LASA1B$bmlength)< 0, NA, as.numeric(LASA1B$bmlength))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_1    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_height_all_1 <- ifelse(as.numeric(LASA1C$cmed150)< 0, NA, as.numeric(LASA1C$cmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined    
**Variable name**: phy_height_all_2    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_height_all_2 <- ifelse(as.numeric(LASA1D$dmed150)< 0, NA, as.numeric(LASA1D$dmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_3    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_height_all_3 <- ifelse(as.numeric(LASA1E$emed150)< 0, NA, as.numeric(LASA1E$emed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_4    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_height_all_4 <- ifelse(as.numeric(LASA1F$fmed150)< 0, NA, as.numeric(LASA1F$fmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_5    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_height_all_5 <- ifelse(as.numeric(LASA1G$gmed150)< 0, NA, as.numeric(LASA1G$gmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_6    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_height_all_6 <- ifelse(as.numeric(LASA1H$HMED150)< 0, NA, as.numeric(LASA1H$HMED150))
```  

### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_ms_0[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))] <- ifelse((as.numeric(LASA1B$bmweight)[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))] <0 | as.numeric(LASA1B$bmlength)[!is.na(as.numeric(LASA1B$bmlength) & !is.na(as.numeric(LASA1B$bmweight)))] <0),NA, (as.numeric(LASA1B$bmweight)[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))]) / ((0.01*as.numeric(LASA1B$bmlength[!is.na(as.numeric(LASA1B$bmlength) & !is.na(as.numeric(LASA1B$bmweight)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_ms_1[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))] <- ifelse((as.numeric(LASA1C$cmed153)[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))] <0 | as.numeric(LASA1C$cmed150)[!is.na(as.numeric(LASA1C$cmed150) & !is.na(as.numeric(LASA1C$cmed153)))] <0),NA, (as.numeric(LASA1C$cmed153)[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))]) / ((0.01*as.numeric(LASA1C$cmed150[!is.na(as.numeric(LASA1C$cmed150) & !is.na(as.numeric(LASA1C$cmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_ms_2[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))] <- ifelse((as.numeric(LASA1D$dmed153)[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))] <0 | as.numeric(LASA1D$dmed150)[!is.na(as.numeric(LASA1D$dmed150) & !is.na(as.numeric(LASA1D$dmed153)))] <0),NA, (as.numeric(LASA1D$dmed153)[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))]) / ((0.01*as.numeric(LASA1D$dmed150[!is.na(as.numeric(LASA1D$dmed150) & !is.na(as.numeric(LASA1D$dmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_ms_3[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))] <- ifelse((as.numeric(LASA1E$emed153)[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))] <0 | as.numeric(LASA1E$emed150)[!is.na(as.numeric(LASA1E$emed150) & !is.na(as.numeric(LASA1E$emed153)))] <0),NA, (as.numeric(LASA1E$emed153)[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))]) / ((0.01*as.numeric(LASA1E$emed150[!is.na(as.numeric(LASA1E$emed150) & !is.na(as.numeric(LASA1E$emed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_ms_4[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))] <- ifelse((as.numeric(LASA1F$fmed153)[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))] <0 | as.numeric(LASA1F$fmed150)[!is.na(as.numeric(LASA1F$fmed150) & !is.na(as.numeric(LASA1F$fmed153)))] <0),NA, (as.numeric(LASA1F$fmed153)[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))]) / ((0.01*as.numeric(LASA1F$fmed150[!is.na(as.numeric(LASA1F$fmed150) & !is.na(as.numeric(LASA1F$fmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_ms_5[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))] <- ifelse((as.numeric(LASA1G$gmed153)[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))] <0 | as.numeric(LASA1G$gmed150)[!is.na(as.numeric(LASA1G$gmed150) & !is.na(as.numeric(LASA1G$gmed153)))] <0),NA, (as.numeric(LASA1G$gmed153)[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))]) / ((0.01*as.numeric(LASA1G$gmed150[!is.na(as.numeric(LASA1G$gmed150) & !is.na(as.numeric(LASA1G$gmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_ms_6[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))] <- ifelse((as.numeric(LASA1H$HMED153)[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))] <0 | as.numeric(LASA1H$HMED150)[!is.na(as.numeric(LASA1H$HMED150) & !is.na(as.numeric(LASA1H$HMED153)))] <0),NA, (as.numeric(LASA1H$HMED153)[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))]) / ((0.01*as.numeric(LASA1H$HMED150[!is.na(as.numeric(LASA1H$HMED150) & !is.na(as.numeric(LASA1H$HMED153)))]))^2))
```  

### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   missing height variable bmvar152 question  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_sr_0[!is.na(as.numeric(LASA1B$bmvar156) & !is.na(as.numeric(LASA1B$bmvar152)))] <- ifelse((as.numeric(LASA1B$bmvar156)[!is.na(as.numeric(LASA1B$bmvar156) & !is.na(as.numeric(LASA1B$bmvar152)))] <0 | as.numeric(LASA1B$bmvar152)[!is.na(as.numeric(LASA1B$bmvar152) & !is.na(as.numeric(LASA1B$bmvar156)))] <0),NA, (as.numeric(LASA1B$bmvar156)[!is.na(as.numeric(LASA1B$bmvar156) & !is.na(as.numeric(LASA1B$bmvar152)))]) / ((0.01*as.numeric(LASA1B$bmvar152[!is.na(as.numeric(LASA1B$bmvar152) & !is.na(as.numeric(LASA1B$bmvar156)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_sr_1[!is.na(as.numeric(LASA1C$cmed155) & !is.na(as.numeric(LASA1C$cmed152)))] <- ifelse((as.numeric(LASA1C$cmed155)[!is.na(as.numeric(LASA1C$cmed155) & !is.na(as.numeric(LASA1C$cmed152)))] <0 | as.numeric(LASA1C$cmed152)[!is.na(as.numeric(LASA1C$cmed152) & !is.na(as.numeric(LASA1C$cmed155)))] <0),NA, (as.numeric(LASA1C$cmed155)[!is.na(as.numeric(LASA1C$cmed155) & !is.na(as.numeric(LASA1C$cmed152)))]) / ((0.01*as.numeric(LASA1C$cmed152[!is.na(as.numeric(LASA1C$cmed152) & !is.na(as.numeric(LASA1C$cmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_sr_2[!is.na(as.numeric(LASA1D$dmed155) & !is.na(as.numeric(LASA1D$dmed152)))] <- ifelse((as.numeric(LASA1D$dmed155)[!is.na(as.numeric(LASA1D$dmed155) & !is.na(as.numeric(LASA1D$dmed152)))] <0 | as.numeric(LASA1D$dmed152)[!is.na(as.numeric(LASA1D$dmed152) & !is.na(as.numeric(LASA1D$dmed155)))] <0),NA, (as.numeric(LASA1D$dmed155)[!is.na(as.numeric(LASA1D$dmed155) & !is.na(as.numeric(LASA1D$dmed152)))]) / ((0.01*as.numeric(LASA1D$dmed152[!is.na(as.numeric(LASA1D$dmed152) & !is.na(as.numeric(LASA1D$dmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_sr_3[!is.na(as.numeric(LASA1E$emed155) & !is.na(as.numeric(LASA1E$emed152)))] <- ifelse((as.numeric(LASA1E$emed155)[!is.na(as.numeric(LASA1E$emed155) & !is.na(as.numeric(LASA1E$emed152)))] <0 | as.numeric(LASA1E$emed152)[!is.na(as.numeric(LASA1E$emed152) & !is.na(as.numeric(LASA1E$emed155)))] <0),NA, (as.numeric(LASA1E$emed155)[!is.na(as.numeric(LASA1E$emed155) & !is.na(as.numeric(LASA1E$emed152)))]) / ((0.01*as.numeric(LASA1E$emed152[!is.na(as.numeric(LASA1E$emed152) & !is.na(as.numeric(LASA1E$emed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_sr_4[!is.na(as.numeric(LASA1F$fmed155) & !is.na(as.numeric(LASA1F$fmed152)))] <- ifelse((as.numeric(LASA1F$fmed155)[!is.na(as.numeric(LASA1F$fmed155) & !is.na(as.numeric(LASA1F$fmed152)))] <0 | as.numeric(LASA1F$fmed152)[!is.na(as.numeric(LASA1F$fmed152) & !is.na(as.numeric(LASA1F$fmed155)))] <0),NA, (as.numeric(LASA1F$fmed155)[!is.na(as.numeric(LASA1F$fmed155) & !is.na(as.numeric(LASA1F$fmed152)))]) / ((0.01*as.numeric(LASA1F$fmed152[!is.na(as.numeric(LASA1F$fmed152) & !is.na(as.numeric(LASA1F$fmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_sr_5[!is.na(as.numeric(LASA1G$gmed155) & !is.na(as.numeric(LASA1G$gmed152)))] <- ifelse((as.numeric(LASA1G$gmed155)[!is.na(as.numeric(LASA1G$gmed155) & !is.na(as.numeric(LASA1G$gmed152)))] <0 | as.numeric(LASA1G$gmed152)[!is.na(as.numeric(LASA1G$gmed152) & !is.na(as.numeric(LASA1G$gmed155)))] <0),NA, (as.numeric(LASA1G$gmed155)[!is.na(as.numeric(LASA1G$gmed155) & !is.na(as.numeric(LASA1G$gmed152)))]) / ((0.01*as.numeric(LASA1G$gmed152[!is.na(as.numeric(LASA1G$gmed152) & !is.na(as.numeric(LASA1G$gmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_sr_6[!is.na(as.numeric(LASA1H$HMED155) & !is.na(as.numeric(LASA1H$HMED152)))] <- ifelse((as.numeric(LASA1H$HMED155)[!is.na(as.numeric(LASA1H$HMED155) & !is.na(as.numeric(LASA1H$HMED152)))] <0 | as.numeric(LASA1H$HMED152)[!is.na(as.numeric(LASA1H$HMED152) & !is.na(as.numeric(LASA1H$HMED155)))] <0),NA, (as.numeric(LASA1H$HMED155)[!is.na(as.numeric(LASA1H$HMED155) & !is.na(as.numeric(LASA1H$HMED152)))]) / ((0.01*as.numeric(LASA1H$HMED152[!is.na(as.numeric(LASA1H$HMED152) & !is.na(as.numeric(LASA1H$HMED155)))]))^2))
```   

### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_all_0[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))] <- ifelse((as.numeric(LASA1B$bmweight)[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))] <0 | as.numeric(LASA1B$bmlength)[!is.na(as.numeric(LASA1B$bmlength) & !is.na(as.numeric(LASA1B$bmweight)))] <0),NA, (as.numeric(LASA1B$bmweight)[!is.na(as.numeric(LASA1B$bmweight) & !is.na(as.numeric(LASA1B$bmlength)))]) / ((0.01*as.numeric(LASA1B$bmlength[!is.na(as.numeric(LASA1B$bmlength) & !is.na(as.numeric(LASA1B$bmweight)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_all_1[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))] <- ifelse((as.numeric(LASA1C$cmed153)[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))] <0 | as.numeric(LASA1C$cmed150)[!is.na(as.numeric(LASA1C$cmed150) & !is.na(as.numeric(LASA1C$cmed153)))] <0),NA, (as.numeric(LASA1C$cmed153)[!is.na(as.numeric(LASA1C$cmed153) & !is.na(as.numeric(LASA1C$cmed150)))]) / ((0.01*as.numeric(LASA1C$cmed150[!is.na(as.numeric(LASA1C$cmed150) & !is.na(as.numeric(LASA1C$cmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.     
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_all_2[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))] <- ifelse((as.numeric(LASA1D$dmed153)[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))] <0 | as.numeric(LASA1D$dmed150)[!is.na(as.numeric(LASA1D$dmed150) & !is.na(as.numeric(LASA1D$dmed153)))] <0),NA, (as.numeric(LASA1D$dmed153)[!is.na(as.numeric(LASA1D$dmed153) & !is.na(as.numeric(LASA1D$dmed150)))]) / ((0.01*as.numeric(LASA1D$dmed150[!is.na(as.numeric(LASA1D$dmed150) & !is.na(as.numeric(LASA1D$dmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_all_3[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))] <- ifelse((as.numeric(LASA1E$emed153)[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))] <0 | as.numeric(LASA1E$emed150)[!is.na(as.numeric(LASA1E$emed150) & !is.na(as.numeric(LASA1E$emed153)))] <0),NA, (as.numeric(LASA1E$emed153)[!is.na(as.numeric(LASA1E$emed153) & !is.na(as.numeric(LASA1E$emed150)))]) / ((0.01*as.numeric(LASA1E$emed150[!is.na(as.numeric(LASA1E$emed150) & !is.na(as.numeric(LASA1E$emed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_all_4[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))] <- ifelse((as.numeric(LASA1F$fmed153)[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))] <0 | as.numeric(LASA1F$fmed150)[!is.na(as.numeric(LASA1F$fmed150) & !is.na(as.numeric(LASA1F$fmed153)))] <0),NA, (as.numeric(LASA1F$fmed153)[!is.na(as.numeric(LASA1F$fmed153) & !is.na(as.numeric(LASA1F$fmed150)))]) / ((0.01*as.numeric(LASA1F$fmed150[!is.na(as.numeric(LASA1F$fmed150) & !is.na(as.numeric(LASA1F$fmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_all_5[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))] <- ifelse((as.numeric(LASA1G$gmed153)[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))] <0 | as.numeric(LASA1G$gmed150)[!is.na(as.numeric(LASA1G$gmed150) & !is.na(as.numeric(LASA1G$gmed153)))] <0),NA, (as.numeric(LASA1G$gmed153)[!is.na(as.numeric(LASA1G$gmed153) & !is.na(as.numeric(LASA1G$gmed150)))]) / ((0.01*as.numeric(LASA1G$gmed150[!is.na(as.numeric(LASA1G$gmed150) & !is.na(as.numeric(LASA1G$gmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_all_6[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))] <- ifelse((as.numeric(LASA1H$HMED153)[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))] <0 | as.numeric(LASA1H$HMED150)[!is.na(as.numeric(LASA1H$HMED150) & !is.na(as.numeric(LASA1H$HMED153)))] <0),NA, (as.numeric(LASA1H$HMED153)[!is.na(as.numeric(LASA1H$HMED153) & !is.na(as.numeric(LASA1H$HMED150)))]) / ((0.01*as.numeric(LASA1H$HMED150[!is.na(as.numeric(LASA1H$HMED150) & !is.na(as.numeric(LASA1H$HMED153)))]))^2))
```  

### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_0  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_cat_ms_0 <- ifelse(oth_LASA1_0$phy_bmi_ms_0 <18.5,0L, ifelse(oth_LASA1_0$phy_bmi_ms_0 <25 & oth_LASA1_0$phy_bmi_ms_0 >= 18.5, 1L, ifelse(oth_LASA1_0$phy_bmi_ms_0 < 30 & oth_LASA1_0$phy_bmi_ms_0 >=25,2L, ifelse(oth_LASA1_0$phy_bmi_ms_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_1  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_cat_ms_1 <- ifelse(oth_LASA1_1$phy_bmi_ms_1 <18.5,0L, ifelse(oth_LASA1_1$phy_bmi_ms_1 <25 & oth_LASA1_1$phy_bmi_ms_1 >= 18.5, 1L, ifelse(oth_LASA1_1$phy_bmi_ms_1 < 30 & oth_LASA1_1$phy_bmi_ms_1 >=25,2L, ifelse(oth_LASA1_1$phy_bmi_ms_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_2  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_cat_ms_2 <- ifelse(oth_LASA1_2$phy_bmi_ms_2 <18.5,0L, ifelse(oth_LASA1_2$phy_bmi_ms_2 <25 & oth_LASA1_2$phy_bmi_ms_2 >= 18.5, 1L, ifelse(oth_LASA1_2$phy_bmi_ms_2 < 30 & oth_LASA1_2$phy_bmi_ms_2 >=25,2L, ifelse(oth_LASA1_2$phy_bmi_ms_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_3  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_cat_ms_3 <- ifelse(oth_LASA1_3$phy_bmi_ms_3 <18.5,0L, ifelse(oth_LASA1_3$phy_bmi_ms_3 <25 & oth_LASA1_3$phy_bmi_ms_3 >= 18.5, 1L, ifelse(oth_LASA1_3$phy_bmi_ms_3 < 30 & oth_LASA1_3$phy_bmi_ms_3 >=25,2L, ifelse(oth_LASA1_3$phy_bmi_ms_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_4  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_cat_ms_4 <- ifelse(oth_LASA1_4$phy_bmi_ms_4 <18.5,0L, ifelse(oth_LASA1_4$phy_bmi_ms_4 <25 & oth_LASA1_4$phy_bmi_ms_4 >= 18.5, 1L, ifelse(oth_LASA1_4$phy_bmi_ms_4 < 30 & oth_LASA1_4$phy_bmi_ms_4 >=25,2L, ifelse(oth_LASA1_4$phy_bmi_ms_4 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_5  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_cat_ms_5 <- ifelse(oth_LASA1_5$phy_bmi_ms_5 <18.5,0L, ifelse(oth_LASA1_5$phy_bmi_ms_5 <25 & oth_LASA1_5$phy_bmi_ms_5 >= 18.5, 1L, ifelse(oth_LASA1_5$phy_bmi_ms_5 < 30 & oth_LASA1_5$phy_bmi_ms_5 >=25,2L, ifelse(oth_LASA1_5$phy_bmi_ms_5 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_6  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_cat_ms_6 <- ifelse(oth_LASA1_6$phy_bmi_ms_6 <18.5,0L, ifelse(oth_LASA1_6$phy_bmi_ms_6 <25 & oth_LASA1_6$phy_bmi_ms_6 >= 18.5, 1L, ifelse(oth_LASA1_6$phy_bmi_ms_6 < 30 & oth_LASA1_6$phy_bmi_ms_6 >=25,2L, ifelse(oth_LASA1_6$phy_bmi_ms_6 >=30,3L,NA))))
```  

### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_cat_sr_0 <- ifelse(oth_LASA1_0$phy_bmi_sr_0 <18.5,0L, ifelse(oth_LASA1_0$phy_bmi_sr_0 <25 & oth_LASA1_0$phy_bmi_sr_0 >= 18.5, 1L, ifelse(oth_LASA1_0$phy_bmi_sr_0 < 30 & oth_LASA1_0$phy_bmi_sr_0 >=25,2L, ifelse(oth_LASA1_0$phy_bmi_sr_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_cat_sr_1 <- ifelse(oth_LASA1_1$phy_bmi_sr_1 <18.5,0L, ifelse(oth_LASA1_1$phy_bmi_sr_1 <25 & oth_LASA1_1$phy_bmi_sr_1 >= 18.5, 1L, ifelse(oth_LASA1_1$phy_bmi_sr_1 < 30 & oth_LASA1_1$phy_bmi_sr_1 >=25,2L, ifelse(oth_LASA1_1$phy_bmi_sr_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_cat_sr_2 <- ifelse(oth_LASA1_2$phy_bmi_sr_2 <18.5,0L, ifelse(oth_LASA1_2$phy_bmi_sr_2 <25 & oth_LASA1_2$phy_bmi_sr_2 >= 18.5, 1L, ifelse(oth_LASA1_2$phy_bmi_sr_2 < 30 & oth_LASA1_2$phy_bmi_sr_2 >=25,2L, ifelse(oth_LASA1_2$phy_bmi_sr_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_cat_sr_3 <- ifelse(oth_LASA1_3$phy_bmi_sr_3 <18.5,0L, ifelse(oth_LASA1_3$phy_bmi_sr_3 <25 & oth_LASA1_3$phy_bmi_sr_3 >= 18.5, 1L, ifelse(oth_LASA1_3$phy_bmi_sr_3 < 30 & oth_LASA1_3$phy_bmi_sr_3 >=25,2L, ifelse(oth_LASA1_3$phy_bmi_sr_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_cat_sr_4 <- ifelse(oth_LASA1_4$phy_bmi_sr_4 <18.5,0L, ifelse(oth_LASA1_4$phy_bmi_sr_4 <25 & oth_LASA1_4$phy_bmi_sr_4 >= 18.5, 1L, ifelse(oth_LASA1_4$phy_bmi_sr_4 < 30 & oth_LASA1_4$phy_bmi_sr_4 >=25,2L, ifelse(oth_LASA1_4$phy_bmi_sr_4 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_cat_sr_5 <- ifelse(oth_LASA1_5$phy_bmi_sr_5 <18.5,0L, ifelse(oth_LASA1_5$phy_bmi_sr_5 <25 & oth_LASA1_5$phy_bmi_sr_5 >= 18.5, 1L, ifelse(oth_LASA1_5$phy_bmi_sr_5 < 30 & oth_LASA1_5$phy_bmi_sr_5 >=25,2L, ifelse(oth_LASA1_5$phy_bmi_sr_5 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_cat_sr_6 <- ifelse(oth_LASA1_6$phy_bmi_sr_6 <18.5,0L, ifelse(oth_LASA1_6$phy_bmi_sr_6 <25 & oth_LASA1_6$phy_bmi_sr_6 >= 18.5, 1L, ifelse(oth_LASA1_6$phy_bmi_sr_6 < 30 & oth_LASA1_6$phy_bmi_sr_6 >=25,2L, ifelse(oth_LASA1_6$phy_bmi_sr_6 >=30,3L,NA))))
```  

### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete    
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_bmi_cat_all_0 <- ifelse(oth_LASA1_0$phy_bmi_ms_0 <18.5,0L, ifelse(oth_LASA1_0$phy_bmi_ms_0 <25 & oth_LASA1_0$phy_bmi_ms_0 >= 18.5, 1L, ifelse(oth_LASA1_0$phy_bmi_ms_0 < 30 & oth_LASA1_0$phy_bmi_ms_0 >=25,2L, ifelse(oth_LASA1_0$phy_bmi_ms_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_bmi_cat_all_1 <- ifelse(oth_LASA1_1$phy_bmi_all_1 <18.5,0L, ifelse(oth_LASA1_1$phy_bmi_all_1 <25 & oth_LASA1_1$phy_bmi_all_1 >= 18.5, 1L, ifelse(oth_LASA1_1$phy_bmi_all_1 < 30 & oth_LASA1_1$phy_bmi_all_1 >=25,2L, ifelse(oth_LASA1_1$phy_bmi_all_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_bmi_cat_all_2 <- ifelse(oth_LASA1_2$phy_bmi_all_2 <18.5,0L, ifelse(oth_LASA1_2$phy_bmi_all_2 <25 & oth_LASA1_2$phy_bmi_all_2 >= 18.5, 1L, ifelse(oth_LASA1_2$phy_bmi_all_2 < 30 & oth_LASA1_2$phy_bmi_all_2 >=25,2L, ifelse(oth_LASA1_2$phy_bmi_all_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_bmi_cat_all_3 <- ifelse(oth_LASA1_3$phy_bmi_all_3 <18.5,0L, ifelse(oth_LASA1_3$phy_bmi_all_3 <25 & oth_LASA1_3$phy_bmi_all_3 >= 18.5, 1L, ifelse(oth_LASA1_3$phy_bmi_all_3 < 30 & oth_LASA1_3$phy_bmi_all_3 >=25,2L, ifelse(oth_LASA1_3$phy_bmi_all_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_bmi_cat_all_4 <- ifelse(oth_LASA1_4$phy_bmi_all_4 <18.5,0L, ifelse(oth_LASA1_4$phy_bmi_all_4 <25 & oth_LASA1_4$phy_bmi_all_4 >= 18.5, 1L, ifelse(oth_LASA1_4$phy_bmi_all_4 < 30 & oth_LASA1_4$phy_bmi_all_4 >=25,2L, ifelse(oth_LASA1_4$phy_bmi_all_4 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_bmi_cat_all_5 <- ifelse(oth_LASA1_5$phy_bmi_all_5 <18.5,0L, ifelse(oth_LASA1_5$phy_bmi_all_5 <25 & oth_LASA1_5$phy_bmi_all_5 >= 18.5, 1L, ifelse(oth_LASA1_5$phy_bmi_all_5 < 30 & oth_LASA1_5$phy_bmi_all_5 >=25,2L, ifelse(oth_LASA1_5$phy_bmi_all_5 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_bmi_cat_all_6 <- ifelse(oth_LASA1_6$phy_bmi_all_6 <18.5,0L, ifelse(oth_LASA1_6$phy_bmi_all_6 <25 & oth_LASA1_6$phy_bmi_all_6 >= 18.5, 1L, ifelse(oth_LASA1_6$phy_bmi_all_6 < 30 & oth_LASA1_6$phy_bmi_all_6 >=25,2L, ifelse(oth_LASA1_6$phy_bmi_all_6 >=30,3L,NA))))
```  

### **Variable label**:  Waist circumference in cm - measured and self-reported combined  
**Variable name**: phy_waist_all_0  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  commplete  
****Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$phy_waist_all_0 <- ifelse(as.numeric(LASA1B$bmwaist)>0,as.numeric(LASA1B$bmwaist),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_1  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.     
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$phy_waist_all_1 <- ifelse(as.numeric(LASA1C$cmed156)>0,as.numeric(LASA1C$cmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_2  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$phy_waist_all_2 <- ifelse(as.numeric(LASA1D$dmed156)>0,as.numeric(LASA1D$dmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_3  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$phy_waist_all_3 <- ifelse(as.numeric(LASA1E$emed156)>0,as.numeric(LASA1E$emed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_4  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:   complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$phy_waist_all_4 <- ifelse(as.numeric(LASA1F$fmed156)>0,as.numeric(LASA1F$fmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_5  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.      
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$phy_waist_all_5 <- ifelse(as.numeric(LASA1G$gmed156)>0,as.numeric(LASA1G$gmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_6  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: complete   
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$phy_waist_all_6 <- ifelse(as.numeric(LASA1H$HMED156)>0,as.numeric(LASA1H$HMED156),NA)
```  

# General perception of health subdomain

### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_0  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$poh_sah_0 <- recode(as.integer(LASA1B$bsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_1  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$poh_sah_1 <- recode(as.integer(LASA1C$csubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_2  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$poh_sah_2 <- recode(as.integer(LASA1D$dsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_3  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$poh_sah_3 <- recode(as.integer(LASA1E$esubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_4  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$poh_sah_4 <- recode(as.integer(LASA1F$fsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_5  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$poh_sah_5 <- recode(as.integer(LASA1G$gsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_6  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$poh_sah_6 <- recode(as.integer(LASA1H$hsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  

### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_0  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$poh_sah_poor_0 <- recode(as.integer(LASA1B$bsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$poh_sah_poor_1 <- recode(as.integer(LASA1C$csubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_2  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$poh_sah_poor_2 <- recode(as.integer(LASA1D$dsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_3  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$poh_sah_poor_3 <- recode(as.integer(LASA1E$esubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$poh_sah_poor_4 <- recode(as.integer(LASA1F$fsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_5  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$poh_sah_poor_5 <- recode(as.integer(LASA1G$gsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_6  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$poh_sah_poor_6 <- recode(as.integer(LASA1H$hsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  

### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_0    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$poh_sah_good_0 <- recode(as.integer(LASA1B$bsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$poh_sah_good_1 <- recode(as.integer(LASA1C$csubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_2    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$poh_sah_good_2 <- recode(as.integer(LASA1D$dsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_3    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$poh_sah_good_3 <- recode(as.integer(LASA1E$esubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$poh_sah_good_4 <- recode(as.integer(LASA1F$fsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_5    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$poh_sah_good_5 <- recode(as.integer(LASA1G$gsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_6    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$poh_sah_good_6 <- recode(as.integer(LASA1H$hsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  


# Disability subdomain

### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_0   
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_0$fct_stairs_diff_0 <- recode(as.integer(LASA1B$badl1a),'1'=1L,'2'=1L,'3'=1L,'4'=0L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$fct_stairs_diff_1 <- recode(as.integer(LASA1C$cadl1a),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$fct_stairs_diff_2 <- recode(as.integer(LASA1D$dadl1a),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  

### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_0  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_1$fct_walk_diff_1 <- recode(as.integer(LASA1C$cadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_2$fct_walk_diff_2 <- recode(as.integer(LASA1D$dadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_3  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_3$fct_walk_diff_3 <- recode(as.integer(LASA1E$eadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_4  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_4$fct_walk_diff_4 <- recode(as.integer(LASA1F$fadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_5  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_5$fct_walk_diff_5 <- recode(as.integer(LASA1G$gadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_6  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA1_6$fct_walk_diff_6 <- recode(as.integer(LASA1H$HADL5A),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
``` 



