---
title: "Other outcomes DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load R libraries
library(opal)
library(tidyverse)
library(epiDisplay)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LUCAS table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'LASA2B', 'LASA.LASA2B', variables=list('bhbd1','bhart05','bhart06','bcva04','bcva03','bdiabe01','bdiabe02','bdiabe03','bdiabe04','bdiabe04','bmweight','bmwaist','bsubhea1','bmed_hyp','bmvar156','bhart10','bcva02','diabe02','bcva01','bmed153','bmed155','bmed150','bmed152','bage','badl1a','badl5a','bmed156','bmed157','byear','bhart01'))
LASA2B <- opal.execute(erasmus_opal,'LASA2B')

opal.assign.table.tibble(erasmus_opal, 'LASA2F', 'LASA.LASA2F', variables=list('fhbd1','fhbd2a','fcva02a','fcva02b','fhart05','fhart06','fcva04','fcva03','fdiabe01','fdiabe02','fdiabe03','fdiabe04','fdiabe04','fmed153','fmed155','fmweight','fmwaist','fsubhea1','fmed152','fmed150','fcva01','fage','fadl1a','fadl5a','fmed156','fmed157','byear','fhart01'))
LASA2F <- opal.execute(erasmus_opal,'LASA2F')

opal.assign.table.tibble(erasmus_opal, 'LASA2G', 'LASA.LASA2G', variables=list('ghbd1','ghbd2a','ghart05','ghart06','gcva04','gcva03','gcva02a','gcva02b','gdiabe01','gdiabe02','gdiabe03','gdiabe04','gdiabe04','gmweight','gmed155','gmed153','gmed152','gmed150','gmwaist','gsubhea1','gmed155','gmed152','gcva01','gage','gadl1a','gadl5a','gmed156','gmed157','byear','ghart01'))
LASA2G <- opal.execute(erasmus_opal,'LASA2G')

opal.assign.table.tibble(erasmus_opal, 'LASA2H', 'LASA.LASA2H', variables=list('HHBD1','HHBD2A','HHART06','HHART05','HCVA02A','HCVA02B','HDIABE01','HDIABE02','HDIABE03','HDIABE04','HMED155','HMED153','HMED150','HMED152','HMED152','hsubhea1','HDIABE01','hage','HADL1A','HADL5A','HMED156','HMED157','byear','HHART01'))
LASA2H <- opal.execute(erasmus_opal,'LASA2H')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
oth_LASA2_0 <- data.frame(id = LASA2B$id)
oth_LASA2_1 <- data.frame(id = LASA2F$id)
oth_LASA2_2 <- data.frame(id = LASA2G$id)
oth_LASA2_3 <- data.frame(id = LASA2H$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [Diabetes subdomain](#diabetes-subdomain)
6. [BMI subdomain](#bmi-subdomain)
7. [General perception of health subdomain](#general-perception-of-health-subdomain)
8. [Disability subdomain](#disability-subdomain)

# Hypertension subdomain

### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_0  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  complete    
**Harmonization comment**:  Currently has hypertension is used. In general once a respondent has hypertension, they are affected by this chronic disease for life.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$dis_hbp_ever_0 <- recode(as.integer(LASA2B$bhbd1),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_1  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  complete  
**Harmonization comment**:   Currently has hypertension is used. In general once a respondent has hypertension, they are affected by this chronic disease for life.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$dis_hbp_ever_1 <- recode(as.integer(LASA2F$fhbd1), '1'=0L,'2'=1L, .default=NA_integer_)
``` 
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_0  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension  


**Harmonization status**: impossible    
**Harmonization comment**:  study-specific variables bhbd2a = Hypertension: taking medication and bmed_hyp= use of antihypertensives. i.e. current use of medication for hypertension.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension  
**Variable name**:  dis_hbp_med_1  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**: impossible  
**Harmonization comment**:  study-specific variables fhbd2a = Hypertension: taking medication and fmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_2  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables ghbd2a = Hypertension: taking medication and gmed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.    
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_3    
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  study-specific variables HHBD2A = Hypertension: taking medication and HMed_hyp = use of antihypertensives. i.e. current use of medication for hypertension.      
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_4  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  impossible   
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_5  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
# Angina subdomain

### **Variable label**: Lifetime occurrence of angina  
**Variable name**:  dis_angina_ever_0  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_1  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_2  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_3  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible      
**Harmonization comment**:  Incompatible: Two study-specific variables available ("heart: chest pain during exertion" and "heart: exertion pain disappears in 10 minutes") however, only studies with self-reported doctor-diagnosis angina were considered for harmonization.  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_4  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible     
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  

# Myocardial infarction subdomain

### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_0  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**:  bhart01 question  
**R script**:  
```{r, echo=TRUE}
#Merging the raw tables LASA2B-LASA2H
MyMerge2 <- function(x,y){
  merge(x,y, by=c("id","byear"),all=TRUE)
}
med_table2 <- Reduce(MyMerge2, list(LASA2B,LASA2F,LASA2G,LASA2H))
#Harmonization scripts to create "ever had mi"
med_table2$dis_mi_ever_0 <- ifelse(as.integer(med_table2$bhart05)==1 | (as.integer(med_table2$bhart05)==-2 & as.integer(med_table2$bhart01)== 1),0L, ifelse(as.integer(med_table2$bhart05)==2,1L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA2_0<-merge(oth_LASA2_0,med_table2[,c("id","dis_mi_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_1  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**: 	fhart01 & fhart05 & dis_mi_ever_0 question  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever had mi"
med_table2$dis_mi_ever_1  <- ifelse(med_table2$dis_mi_ever_0==1 | (med_table2$dis_mi_ever_0==0 & as.integer(med_table2$fhart05)==2),1L, ifelse(as.integer(med_table2$fhart01)==0 | (med_table2$dis_mi_ever_0==0 & (as.integer(med_table2$fhart01)== 2 | as.integer(med_table2$fhart01)== 3) & as.integer(med_table2$fhart05)==1),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA2_1<-merge(oth_LASA2_1,med_table[,c("id","dis_mi_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_2  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  
**Harmonization comment**: 	dhart01 & dhart05 & dis_mi_ever_1 question  
**R script**:  
```{r, echo=TRUE}
#Harmonization scripts to create "ever had mi"
med_table2$dis_mi_ever_2  <- ifelse(med_table2$dis_mi_ever_1==1 | (med_table2$dis_mi_ever_1==0 & as.integer(med_table2$ghart05)==2),1L, ifelse(as.integer(med_table2$ghart01)==0 | (med_table2$dis_mi_ever_1==0 & (as.integer(med_table2$ghart01)== 2 | as.integer(med_table2$ghart01)== 3) & as.integer(med_table2$ghart05)==1),0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_LASA2_2<-merge(oth_LASA2_2,med_table[,c("id","dis_mi_ever_2")],by="id",all.x=TRUE)
```  

### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_0  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_1  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_2  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  impossible    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
# Stroke subdomain

### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_0  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$dis_stroke_ever_0 <- recode(as.integer(LASA2B$bcva01),'1'=0L,'2'=1L,.default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_1  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$dis_stroke_ever_1 <- recode(as.integer(LASA2F$fcva01),'0'=0L,'1'=1L,'2'=1L,'3'=1L,.default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_2  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$dis_stroke_ever_2 <- recode(as.integer(LASA2G$gcva01),'0'=0L,'1'=1L,'2'=1L,'3'=1L,.default=NA_integer_)
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_0  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  bcva02b (CVA: how many times), if =1-->bcva03j (if 1 stroke, year), if =2-->bcva04j (if 1 strong, first stroke year)
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_1  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**: fcva02b (number of strokes) fcva01:(CVA) fcva02a:(stroke since last interview), fcva03j: (CVA: 1, stroke year), fcva04j:(CVA: > 1, first stroke year), fage (Age at LASA main/telephonic interview (w3)), fmage (Age at LASA medical interview (w3)) collection years 1995-1996
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_2  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**: gcva01 (CVA), gcva02a (CVA: stroke since last interview), gcva02b (CVA: no of strokes), gcva04j (CVA: > 1, first stroke year), gcva03j (CVA: 1, stroke year), collection years 1998-1999
**R script**:  
```{r, echo=TRUE}

```  


# Diabetes subdomain  

### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar  
**Variable name**: dis_diab_ever_0  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Currently has diabetes is used. In general once a respondent has diabetes, they are affected by this chronic disease for life.  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_0$dis_diab_ever_0 <- recode(as.integer(LASA2B$bdiabe01), '1'=0L, '2'=1L, .default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: dis_diab_ever_1  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_1$dis_diab_ever_1 <- recode(as.integer(LASA2F$fdiabe01), '0'=0L, '1'=1L, '2'=1L, '3'=1L, .default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_2  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_2$dis_diab_ever_2 <- recode(as.integer(LASA2G$gdiabe01), '0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: dis_diab_ever_3  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_3$dis_diab_ever_3 <- recode(as.integer(LASA2H$HDIABE01),'0'=0L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_4  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}  
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_5  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_0    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_0$dis_diab_age_0 <- ifelse(as.integer(LASA2B$bdiabe02)<0,NA,as.integer(LASA2B$bdiabe02))
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_1    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_1$dis_diab_age_1 <- ifelse(as.integer(LASA2F$fdiabe02)<0,NA,as.integer(LASA2F$fdiabe02))
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_2    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_2$dis_diab_age_2 <- ifelse(as.integer(LASA2G$gdiabe02)<0,NA,as.integer(LASA2G$gdiabe02))
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_3    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_LASA2_3$dis_diab_age_3 <- ifelse(as.integer(LASA2H$HDIABE02)<0,NA,as.integer(LASA2H$HDIABE02))
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_4    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_5    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible    
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  

### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_0  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA2_0$dis_diab_tx_0<- ifelse(as.integer(LASA2B$bdiabe03)==1 & as.integer(LASA2B$bdiabe04)==1,0L,
                             ifelse(as.integer(LASA2B$bdiabe03)==2 | as.integer(LASA2B$bdiabe03)==3 |
                                    as.integer(LASA2B$bdiabe04)==2 | as.integer(LASA2B$bdiabe04)==3,1L,NA))
``` 
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_1  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA2_1$dis_diab_tx_1<- ifelse(as.integer(LASA2F$fdiabe03)==1 & as.integer(LASA2F$fdiabe04)==1,0L,
                             ifelse(as.integer(LASA2F$fdiabe03)==2 | as.integer(LASA2F$fdiabe03)==3 |
                                    as.integer(LASA2F$fdiabe04)==2 | as.integer(LASA2F$fdiabe04)==3,1L,NA))
``` 
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_2  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA2_2$dis_diab_tx_2<- ifelse(as.integer(LASA2G$gdiabe03)==1 & as.integer(LASA2G$gdiabe04)==1,0L,
                             ifelse(as.integer(LASA2G$gdiabe03)==2 | as.integer(LASA2G$gdiabe03)==3 |
                                    as.integer(LASA2G$gdiabe04)==2 | as.integer(LASA2G$gdiabe04)==3,1L,NA))
``` 
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_3  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  Two variables are used for harmonization "Diabetes-taking medication" categorized as: No | Yes, insulin injections | Yes, tablets only and "Diabetes: treatment doctor" categorized as: No | Yes, family physician | Yes, specialist.  
**R script**:
```{r, echo=TRUE}
oth_LASA2_3$dis_diab_tx_3<- ifelse(as.integer(LASA2H$HDIABE03)==1 & as.integer(LASA2H$HDIABE04)==1,0L,
                             ifelse(as.integer(LASA2H$HDIABE03)==2 | as.integer(LASA2H$HDIABE03)==3 |
                                    as.integer(LASA2H$HDIABE04)==2 | as.integer(LASA2H$HDIABE04)==3,1L,NA))
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_4  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible    
**Harmonization comment**:    
**R script**:
```{r, echo=TRUE}

```    
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_5  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible    
**Harmonization comment**:    
**R script**:
```{r, echo=TRUE}

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_0  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question  
**R script**:
```{r, echo=TRUE}
oth_LASA2_0$dis_diab_tx_0 <- recode(as.integer(LASA2B$bdiabe03),'1'=0L,'2'=1L,'3'=0L, .default=NA_integer_)
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_1  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question  
**R script**:
```{r, echo=TRUE}
oth_LASA2_1$dis_diab_tx_1 <- recode(as.integer(LASA2F$fdiabe03),'1'=0L,'2'=1L,'3'=0L, .default=NA_integer_)
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_2  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  categories of study-specific variable (Diabetes-taking medication) are No | Yes, insulin injections | Yes, tablets only. If does not do treatment, coded as NA. question  
**R script**:
```{r, echo=TRUE}
oth_LASA2_2$dis_diab_tx_2 <- recode(as.integer(LASA2G$gdiabe03),'1'=0L,'2'=1L,'3'=0L, .default=NA_integer_)
```  
# BMI subdomain

### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_0  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_weight_ms_0 <- ifelse(as.numeric(LASA2B$bmed153)< 0.0, NA, as.numeric(LASA2B$bmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_1  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_weight_ms_1 <- ifelse(as.numeric(LASA2F$fmed153)< 0.0, NA, as.numeric(LASA2F$fmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_2  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_weight_ms_2 <- ifelse(as.numeric(LASA2G$gmed153)< 0.0, NA, as.numeric(LASA2G$gmed153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_3  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_weight_ms_3 <- ifelse(as.numeric(LASA2H$HMED153)< 0.0, NA, as.numeric(LASA2H$HMED153))
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_4  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_5  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_6  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_0    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Three participants have values for self-reported weight.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_weight_sr_0 <- ifelse(as.numeric(LASA2B$bmed155)< 0.0, NA, as.numeric(LASA2B$bmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_1    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Four participants have values for self-reported weight.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_weight_sr_1 <- ifelse(as.numeric(LASA2F$fmed155)< 0.0, NA, as.numeric(LASA2F$fmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_2    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Six participants have values for self-reported weight.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_weight_sr_2 <- ifelse(as.numeric(LASA2G$gmed155)< 0.0, NA, as.numeric(LASA2G$gmed155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_3    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Four participants have values for self-reported weight.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_weight_sr_3 <- ifelse(as.numeric(LASA2H$HMED155)< 0.0, NA, as.numeric(LASA2H$HMED155))
```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_4    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_5    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_6    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_0      
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_weight_all_0 <- ifelse(as.numeric(LASA2B$bmed153)< 0.0, NA, as.numeric(LASA2B$bmed153))
```
### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_1    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.     
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_weight_all_1 <- ifelse(as.numeric(LASA2F$fmed153)< 0.0, NA, as.numeric(LASA2F$fmed153))
```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_2    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.      
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_weight_all_2 <- ifelse(as.numeric(LASA2G$gmed153)< 0.0, NA, as.numeric(LASA2G$gmed153))
```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_3     
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.   
**Value type**: decimal   
**Variable unit**: kg    
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_weight_all_3 <- ifelse(as.numeric(LASA2H$HMED153)< 0.0, NA, as.numeric(LASA2H$HMED153))
```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_4    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.    
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_5    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.      
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_6    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported were collected, measured weight was taken.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_0  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_height_ms_0 <- ifelse(as.numeric(LASA2B$bmed150)<0.0,NA,as.numeric(LASA2B$bmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_1  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_height_ms_1 <- ifelse(as.numeric(LASA2F$fmed150)< 0.0, NA, as.numeric(LASA2F$fmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_2  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_height_ms_2 <- ifelse(as.numeric(LASA2G$gmed150)< 0.0, NA, as.numeric(LASA2G$gmed150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_3  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm    
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_height_ms_3 <- ifelse(as.numeric(LASA2H$HMED150)< 0.0, NA, as.numeric(LASA2H$HMED150))
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_4  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_5  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_6  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_0  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:   One participant has value for self-reported height.    
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_height_sr_0 <- ifelse(as.numeric(LASA2B$bmed152)<0.0,NA,as.numeric(LASA2B$bmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_1  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:  Three participants have values for self-reported height.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_height_sr_1 <- ifelse(as.numeric(LASA2F$fmed152)< 0.0, NA, as.numeric(LASA2F$fmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_2  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Three participants have values for self-reported height.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_height_sr_2 <- ifelse(as.numeric(LASA2G$gmed152)< 0.0, NA, as.numeric(LASA2G$gmed152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_3  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Two participants have values for self-reported height.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_height_sr_3 <- ifelse(as.numeric(LASA2H$HMED152)< 0.0, NA, as.numeric(LASA2H$HMED152))
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_4  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_5  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_6  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_0    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.     
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete      
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_height_all_0 <- ifelse(as.numeric(LASA2B$bmed150)<0.0,NA,as.numeric(LASA2B$bmed150))
```   
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_1    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_height_all_1 <- ifelse(as.numeric(LASA2F$fmed150)< 0.0, NA, as.numeric(LASA2F$fmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined    
**Variable name**: phy_height_all_2    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_height_all_2 <- ifelse(as.numeric(LASA2G$gmed150)< 0.0, NA, as.numeric(LASA2G$gmed150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_3    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_height_all_3 <- ifelse(as.numeric(LASA2H$HMED150)< 0.0, NA, as.numeric(LASA2H$HMED150))
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_4    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_5    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_6    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

``` 

### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_ms_0[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))] <- ifelse((as.numeric(LASA2B$bmed153)[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))] <0 | as.numeric(LASA2B$bmed150)[!is.na(as.numeric(LASA2B$bmed150) & !is.na(as.numeric(LASA2B$bmed153)))] <0),NA, (as.numeric(LASA2B$bmed153)[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))]) / ((0.01*as.numeric(LASA2B$bmed150[!is.na(as.numeric(LASA2B$bmed150) & !is.na(as.numeric(LASA2B$bmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_ms_1[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))] <- ifelse((as.numeric(LASA2F$fmed153)[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))] <0 | as.numeric(LASA2F$fmed150)[!is.na(as.numeric(LASA2F$fmed150) & !is.na(as.numeric(LASA2F$fmed153)))] <0),NA, (as.numeric(LASA2F$fmed153)[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))]) / ((0.01*as.numeric(LASA2F$fmed150[!is.na(as.numeric(LASA2F$fmed150) & !is.na(as.numeric(LASA2F$fmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_ms_2[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))] <- ifelse((as.numeric(LASA2G$gmed153)[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))] <0 | as.numeric(LASA2G$gmed150)[!is.na(as.numeric(LASA2G$gmed150) & !is.na(as.numeric(LASA2G$gmed153)))] <0),NA, (as.numeric(LASA2G$gmed153)[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))]) / ((0.01*as.numeric(LASA2G$gmed150[!is.na(as.numeric(LASA2G$gmed150) & !is.na(as.numeric(LASA2G$gmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_ms_3[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))] <- ifelse((as.numeric(LASA2H$HMED153)[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))] <0 | as.numeric(LASA2H$HMED150)[!is.na(as.numeric(LASA2H$HMED150) & !is.na(as.numeric(LASA2H$HMED153)))] <0),NA, (as.numeric(LASA2H$HMED153)[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))]) / ((0.01*as.numeric(LASA2H$HMED150[!is.na(as.numeric(LASA2H$HMED150) & !is.na(as.numeric(LASA2H$HMED153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   One pariticpant has value for self-reported BMI.    
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_sr_0[!is.na(as.numeric(LASA2B$bmed155) & !is.na(as.numeric(LASA2B$bmed152)))] <- ifelse((as.numeric(LASA2B$bmed155)[!is.na(as.numeric(LASA2B$bmed155) & !is.na(as.numeric(LASA2B$bmed152)))] <0 | as.numeric(LASA2B$bmed152)[!is.na(as.numeric(LASA2B$bmed152) & !is.na(as.numeric(LASA2B$bmed155)))] <0),NA, (as.numeric(LASA2B$bmed155)[!is.na(as.numeric(LASA2B$bmed155) & !is.na(as.numeric(LASA2B$bmed152)))]) / ((0.01*as.numeric(LASA2B$bmed152[!is.na(as.numeric(LASA2B$bmed152) & !is.na(as.numeric(LASA2B$bmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   One pariticpant has value for self-reported BMI.    
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_sr_1[!is.na(as.numeric(LASA2F$fmed155) & !is.na(as.numeric(LASA2F$fmed152)))] <- ifelse((as.numeric(LASA2F$fmed155)[!is.na(as.numeric(LASA2F$fmed155) & !is.na(as.numeric(LASA2F$fmed152)))] <0 | as.numeric(LASA2F$fmed152)[!is.na(as.numeric(LASA2F$fmed152) & !is.na(as.numeric(LASA2F$fmed155)))] <0),NA, (as.numeric(LASA2F$fmed155)[!is.na(as.numeric(LASA2F$fmed155) & !is.na(as.numeric(LASA2F$fmed152)))]) / ((0.01*as.numeric(LASA2F$fmed152[!is.na(as.numeric(LASA2F$fmed152) & !is.na(as.numeric(LASA2F$fmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   Three participants have values for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_sr_2[!is.na(as.numeric(LASA2G$gmed155) & !is.na(as.numeric(LASA2G$gmed152)))] <- ifelse((as.numeric(LASA2G$gmed155)[!is.na(as.numeric(LASA2G$gmed155) & !is.na(as.numeric(LASA2G$gmed152)))] <0 | as.numeric(LASA2G$gmed152)[!is.na(as.numeric(LASA2G$gmed152) & !is.na(as.numeric(LASA2G$gmed155)))] <0),NA, (as.numeric(LASA2G$gmed155)[!is.na(as.numeric(LASA2G$gmed155) & !is.na(as.numeric(LASA2G$gmed152)))]) / ((0.01*as.numeric(LASA2G$gmed152[!is.na(as.numeric(LASA2G$gmed152) & !is.na(as.numeric(LASA2G$gmed155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   One participant has value for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_sr_3[!is.na(as.numeric(LASA2H$HMED155) & !is.na(as.numeric(LASA2H$HMED152)))] <- ifelse((as.numeric(LASA2H$HMED155)[!is.na(as.numeric(LASA2H$HMED155) & !is.na(as.numeric(LASA2H$HMED152)))] <0 | as.numeric(LASA2H$HMED152)[!is.na(as.numeric(LASA2H$HMED152) & !is.na(as.numeric(LASA2H$HMED155)))] <0),NA, (as.numeric(LASA2H$HMED155)[!is.na(as.numeric(LASA2H$HMED155) & !is.na(as.numeric(LASA2H$HMED152)))]) / ((0.01*as.numeric(LASA2H$HMED152[!is.na(as.numeric(LASA2H$HMED152) & !is.na(as.numeric(LASA2H$HMED155)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_all_0[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))] <- ifelse((as.numeric(LASA2B$bmed153)[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))] <0 | as.numeric(LASA2B$bmed150)[!is.na(as.numeric(LASA2B$bmed150) & !is.na(as.numeric(LASA2B$bmed153)))] <0),NA, (as.numeric(LASA2B$bmed153)[!is.na(as.numeric(LASA2B$bmed153) & !is.na(as.numeric(LASA2B$bmed150)))]) / ((0.01*as.numeric(LASA2B$bmed150[!is.na(as.numeric(LASA2B$bmed150) & !is.na(as.numeric(LASA2B$bmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_all_1[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))] <- ifelse((as.numeric(LASA2F$fmed153)[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))] <0 | as.numeric(LASA2F$fmed150)[!is.na(as.numeric(LASA2F$fmed150) & !is.na(as.numeric(LASA2F$fmed153)))] <0),NA, (as.numeric(LASA2F$fmed153)[!is.na(as.numeric(LASA2F$fmed153) & !is.na(as.numeric(LASA2F$fmed150)))]) / ((0.01*as.numeric(LASA2F$fmed150[!is.na(as.numeric(LASA2F$fmed150) & !is.na(as.numeric(LASA2F$fmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.     
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_all_2[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))] <- ifelse((as.numeric(LASA2G$gmed153)[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))] <0 | as.numeric(LASA2G$gmed150)[!is.na(as.numeric(LASA2G$gmed150) & !is.na(as.numeric(LASA2G$gmed153)))] <0),NA, (as.numeric(LASA2G$gmed153)[!is.na(as.numeric(LASA2G$gmed153) & !is.na(as.numeric(LASA2G$gmed150)))]) / ((0.01*as.numeric(LASA2G$gmed150[!is.na(as.numeric(LASA2G$gmed150) & !is.na(as.numeric(LASA2G$gmed153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_all_3[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))] <- ifelse((as.numeric(LASA2H$HMED153)[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))] <0 | as.numeric(LASA2H$HMED150)[!is.na(as.numeric(LASA2H$HMED150) & !is.na(as.numeric(LASA2H$HMED153)))] <0),NA, (as.numeric(LASA2H$HMED153)[!is.na(as.numeric(LASA2H$HMED153) & !is.na(as.numeric(LASA2H$HMED150)))]) / ((0.01*as.numeric(LASA2H$HMED150[!is.na(as.numeric(LASA2H$HMED150) & !is.na(as.numeric(LASA2H$HMED153)))]))^2))
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_0  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_cat_ms_0 <- ifelse(oth_LASA2_0$phy_bmi_ms_0 <18.5,0L, ifelse(oth_LASA2_0$phy_bmi_ms_0 <25 & oth_LASA2_0$phy_bmi_ms_0 >= 18.5, 1L, ifelse(oth_LASA2_0$phy_bmi_ms_0 < 30 & oth_LASA2_0$phy_bmi_ms_0 >=25,2L, ifelse(oth_LASA2_0$phy_bmi_ms_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_1  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_cat_ms_1 <- ifelse(oth_LASA2_1$phy_bmi_ms_1 <18.5,0L, ifelse(oth_LASA2_1$phy_bmi_ms_1 <25 & oth_LASA2_1$phy_bmi_ms_1 >= 18.5, 1L, ifelse(oth_LASA2_1$phy_bmi_ms_1 < 30 & oth_LASA2_1$phy_bmi_ms_1 >=25,2L, ifelse(oth_LASA2_1$phy_bmi_ms_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_2  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_cat_ms_2 <- ifelse(oth_LASA2_2$phy_bmi_ms_2 <18.5,0L, ifelse(oth_LASA2_2$phy_bmi_ms_2 <25 & oth_LASA2_2$phy_bmi_ms_2 >= 18.5, 1L, ifelse(oth_LASA2_2$phy_bmi_ms_2 < 30 & oth_LASA2_2$phy_bmi_ms_2 >=25,2L, ifelse(oth_LASA2_2$phy_bmi_ms_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_3  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_cat_ms_3 <- ifelse(oth_LASA2_3$phy_bmi_ms_3 <18.5,0L, ifelse(oth_LASA2_3$phy_bmi_ms_3 <25 & oth_LASA2_3$phy_bmi_ms_3 >= 18.5, 1L, ifelse(oth_LASA2_3$phy_bmi_ms_3 < 30 & oth_LASA2_3$phy_bmi_ms_3 >=25,2L, ifelse(oth_LASA2_3$phy_bmi_ms_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_4  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_5  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_6  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   One participant has value for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_cat_sr_0 <- ifelse(oth_LASA2_0$phy_bmi_sr_0 <18.5,0L, ifelse(oth_LASA2_0$phy_bmi_sr_0 <25 & oth_LASA2_0$phy_bmi_sr_0 >= 18.5, 1L, ifelse(oth_LASA2_0$phy_bmi_sr_0 < 30 & oth_LASA2_0$phy_bmi_sr_0 >=25,2L, ifelse(oth_LASA2_0$phy_bmi_sr_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   One participant has value for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_cat_sr_1 <- ifelse(oth_LASA2_1$phy_bmi_sr_1 <18.5,0L, ifelse(oth_LASA2_1$phy_bmi_sr_1 <25 & oth_LASA2_1$phy_bmi_sr_1 >= 18.5, 1L, ifelse(oth_LASA2_1$phy_bmi_sr_1 < 30 & oth_LASA2_1$phy_bmi_sr_1 >=25,2L, ifelse(oth_LASA2_1$phy_bmi_sr_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   Three participants have values for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_cat_sr_2 <- ifelse(oth_LASA2_2$phy_bmi_sr_2 <18.5,0L, ifelse(oth_LASA2_2$phy_bmi_sr_2 <25 & oth_LASA2_2$phy_bmi_sr_2 >= 18.5, 1L, ifelse(oth_LASA2_2$phy_bmi_sr_2 < 30 & oth_LASA2_2$phy_bmi_sr_2 >=25,2L, ifelse(oth_LASA2_2$phy_bmi_sr_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   One participant has value for self-reported BMI.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_cat_sr_3 <- ifelse(oth_LASA2_3$phy_bmi_sr_3 <18.5,0L, ifelse(oth_LASA2_3$phy_bmi_sr_3 <25 & oth_LASA2_3$phy_bmi_sr_3 >= 18.5, 1L, ifelse(oth_LASA2_3$phy_bmi_sr_3 < 30 & oth_LASA2_3$phy_bmi_sr_3 >=25,2L, ifelse(oth_LASA2_3$phy_bmi_sr_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_bmi_cat_all_0 <- ifelse(oth_LASA2_0$phy_bmi_ms_0 <18.5,0L, ifelse(oth_LASA2_0$phy_bmi_ms_0 <25 & oth_LASA2_0$phy_bmi_ms_0 >= 18.5, 1L, ifelse(oth_LASA2_0$phy_bmi_ms_0 < 30 & oth_LASA2_0$phy_bmi_ms_0 >=25,2L, ifelse(oth_LASA2_0$phy_bmi_ms_0 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_bmi_cat_all_1 <- ifelse(oth_LASA2_1$phy_bmi_ms_1 <18.5,0L, ifelse(oth_LASA2_1$phy_bmi_ms_1 <25 & oth_LASA2_1$phy_bmi_ms_1 >= 18.5, 1L, ifelse(oth_LASA2_1$phy_bmi_ms_1 < 30 & oth_LASA2_1$phy_bmi_ms_1 >=25,2L, ifelse(oth_LASA2_1$phy_bmi_ms_1 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_bmi_cat_all_2 <- ifelse(oth_LASA2_2$phy_bmi_ms_2 <18.5,0L, ifelse(oth_LASA2_2$phy_bmi_ms_2 <25 & oth_LASA2_2$phy_bmi_ms_2 >= 18.5, 1L, ifelse(oth_LASA2_2$phy_bmi_ms_2 < 30 & oth_LASA2_2$phy_bmi_ms_2 >=25,2L, ifelse(oth_LASA2_2$phy_bmi_ms_2 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_bmi_cat_all_3 <- ifelse(oth_LASA2_3$phy_bmi_ms_3 <18.5,0L, ifelse(oth_LASA2_3$phy_bmi_ms_3 <25 & oth_LASA2_3$phy_bmi_ms_3 >= 18.5, 1L, ifelse(oth_LASA2_3$phy_bmi_ms_3 < 30 & oth_LASA2_3$phy_bmi_ms_3 >=25,2L, ifelse(oth_LASA2_3$phy_bmi_ms_3 >=30,3L,NA))))
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.   
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Waist circumference in cm - measured and self-reported combined  
**Variable name**: phy_waist_all_0  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:    complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$phy_waist_all_0 <- ifelse(as.numeric(LASA2B$bmed156)>0,as.numeric(LASA2B$bmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_1  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$phy_waist_all_1 <- ifelse(as.numeric(LASA2F$fmed156)>0,as.numeric(LASA2F$fmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_2  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$phy_waist_all_2 <- ifelse(as.numeric(LASA2G$gmed156)>0,as.numeric(LASA2G$gmed156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_3  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   This study has two waist circumference measurements. The first measurement was taken.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$phy_waist_all_3 <- ifelse(as.numeric(LASA2H$HMED156)>0,as.numeric(LASA2H$HMED156),NA)
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_4  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_5  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.      
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_6  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# General perception of health subdomain

### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_0  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$poh_sah_0 <- recode(as.integer(LASA2B$bsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_1  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$poh_sah_1 <- recode(as.integer(LASA2F$fsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_2  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$poh_sah_2 <- recode(as.integer(LASA2G$gsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_3  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$poh_sah_3 <- recode(as.integer(LASA2H$hsubhea1),'1'=0L,'2'=0L,'1'=1L,'4'=1L,'5'=3L,.default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_4  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_5  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_6  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_0  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$poh_sah_poor_0 <- recode(as.integer(LASA2B$bsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$poh_sah_poor_1<- recode(as.integer(LASA2F$fsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_2  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$poh_sah_poor_2 <- recode(as.integer(LASA2G$gsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_3  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$poh_sah_poor_3 <- recode(as.integer(LASA2H$hsubhea1),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_5  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_6  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_0    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$poh_sah_good_0 <- recode(as.integer(LASA2B$bsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$poh_sah_good_1 <- recode(as.integer(LASA2F$fsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_2    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$poh_sah_good_2 <- recode(as.integer(LASA2G$gsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_3    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$poh_sah_good_3 <- recode(as.integer(LASA2H$hsubhea1),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_5    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_6    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  


# Disability subdomain

### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_0   
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$fct_stairs_diff_0 <- recode(as.integer(LASA2B$badl1a),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$fct_stairs_diff_1 <- recode(as.integer(LASA2F$fadl1a),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**: Study-specific variable is Stairs: 15 steps without stopping.  
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$fct_stairs_diff_2 <- recode(as.integer(LASA2G$gadl1a),'1'=1L,'2'=1L,'3'=1L,'4'=1L,'5'=0L,.default=NA_integer_)
```  

### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_0  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_0$fct_walk_diff_0 <- recode(as.integer(LASA2B$badl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_1$fct_walk_diff_1 <- recode(as.integer(LASA2F$fadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_2$fct_walk_diff_2 <- recode(as.integer(LASA2G$gadl5a),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_3  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variable is Walking: 5 min. outside the house.   
**R script**:  
```{r, echo=TRUE}
oth_LASA2_3$fct_walk_diff_3 <- recode(as.integer(LASA2H$HADL5A),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,.default=NA_integer_)
``` 
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_4  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_5  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_6  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  



