---
title: "Other outcomes DataSchema"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opalr)
library(tidyverse)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment

# CLSA Comprehensive BASELINE
opal.assign.table.tibble(erasmus_opal, 'CoP4_Baseline','CLSA_1.CoP4_Baseline', variables =list("WGT_WEIGHT1_KG_COM", "WGT_WEIGHT2_KG_COM", "WGT_WEIGHT_KG_COM", "HGT_HEIGHT_M_COM","HWT_DISW_COM", "HWT_DBMI_COM", "WHC_WAIST_CM_COM", "WHC_CLTHLAYERS_COM", "GEN_HLTH_COM", "FUL_FSTR_COM", "FUL_WK23B_COM", "CCC_HBP_COM", "HBP_EVRMED_COM", "CCC_ANGI_COM", "CCC_AMI_COM", "IHD_AMIAGE_NB_COM", "CCC_CVA_COM", "STR_CVAAGE_NB_COM", "DIA_DIAB_COM", "DIA_AGE_NB_COM", "DIA_MED_COM", 
"DIA_MEDINSNAME_HUMU_COM", "DIA_MEDINSNAME_LEVE_COM", "DIA_MEDINSNAME_HUMA_COM", "DIA_MEDINSNAME_NOVOR_COM",
"DIA_MEDINSNAME_NOVOM_COM","DIA_MEDINSNAME_LANT_COM","DIA_MEDINSNAME_OT_COM","DIA_MEDAGE_NB_COM"))

CLSA_cop_0 <- opal.execute(erasmus_opal,'CoP4_Baseline')

# CLSA Comprehensive FU1
opal.assign.table.tibble(erasmus_opal, 'CoP_FU1','CLSA_1.CoP_FU1',  variables=list("startlanguage_COF1",
"WGT_WEIGHT1_KG_COF1", "WGT_WEIGHT2_KG_COF1","GEN_HLTH_COF1", "WGT_WEIGHT_KG_COF1", "HGT_HEIGHT_M_COF1","HWT_DBMI_COF1", "WHC_WAIST_CM_COF1", "WHC_CLTHLAYERS_COF1", "FUL_FSTR_COF1", "FUL_WK23B_COF1", "CCC_HBP_COF1", "HBP_EVRMED_COF1", "CCC_ANGI_COF1", "CCC_AMI_COF1", "IHD_AMIAGE_NB_COF1", "CCC_CVA_COF1", "STR_CVAAGE_NB_COF1", "DIA_DIAB_COF1", "DIA_AGE_NB_COF1", "DIA_MED_COF1", "HWT_DISW_COF1",
"DIA_MEDINSNAME_HUMU_COF1", "DIA_MEDINSNAME_LEVE_COF1", "DIA_MEDINSNAME_HUMA_COF1", "DIA_MEDINSNAME_NOVOR_COF1",
"DIA_MEDINSNAME_NOVOM_COF1","DIA_MEDINSNAME_LANT_COF1","DIA_MEDINSNAME_OT_COF1","DIA_MEDAGE_NB_COF1", "PSD_DCTOFF_COM", "WGT_WEIGHTSR_KG_COF1", "HGT_HEIGHT_M_COF1", "HGT_HEIGHTSR_CM_COF1", "HWT_DBMI_COF1"))

#opal.assign.table.tibble(erasmus_opal, 'CoP_FU1','CLSA_1.CoP_FU1',  variables=NULL)
CLSA_cop_1 <- opal.execute(erasmus_opal,'CoP_FU1')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
oth_CLSA_cop_0 <- data.frame(id = CLSA_cop_0$id)
oth_CLSA_cop_1 <- data.frame(id = CLSA_cop_1$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal)
```

# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [Diabetes subdomain](#diabetes-subdomain)
6. [BMI subdomain](#bmi-subdomain)
7. [General perception of health subdomain](#general-perception-of-health-subdomain)
8. [Disability subdomain](#disability-subdomain)

# Hypertension subdomain

### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_0  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  complete  
**Harmonization comment**:   The harmonized variable "Lifetime occurrence of high blood pressure or hypertension" for followup wave was created using "Lifetime occurrence of high blood pressure or hypertension" from baseline and followup wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  

**R script**:  
```{r, echo=TRUE}
#HYPERTENSION VARIABLE
MyMerge <- function(x,y){
  merge(x,y, by= c("id"),all=TRUE)
}
med_table <- Reduce(MyMerge, list(CLSA_cop_0, CLSA_cop_1))
#Harmonization scripts to create "ever had "
med_table$dis_hbp_ever_0 <- recode(as.integer(med_table$CCC_HBP_COM),"1"=1L,"2"=0L,.default=NA_integer_)
#oth_CLSA_cop_0$dis_hbp_ever_0test
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_hbp_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_1  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  complete  
**Harmonization comment**:   The harmonized variable "Lifetime occurrence of high blood pressure or hypertension" for followup wave was created using "Lifetime occurrence of high blood pressure or hypertension" from baseline and followup wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
med_table$dis_hbp_ever_1<- ifelse(med_table$dis_hbp_ever_0==1 | med_table$CCC_HBP_COF1=="1",1L,
                           ifelse(med_table$dis_hbp_ever_0==0 & med_table$CCC_HBP_COF1=="2",0L, NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_hbp_ever_1")],by="id",all.x=TRUE)
``` 
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_0  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension  


**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "participant has ever taken medication for high blood pressure or hypertension" for the followup wave was created using "participant has ever taken medication for high blood pressure or hypertension" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
med_table$dis_hbp_med_0 <- recode(as.integer(med_table$HBP_EVRMED_COM),"1"=1L,"2"=0L,.default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_hbp_med_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Medication for high blood pressure or hypertension  
**Variable name**:  dis_hbp_med_1  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  complete  
**Harmonization comment**:   The harmonized variable "participant has ever taken medication for high blood pressure or hypertension" for the followup wave was created using "participant has ever taken medication for high blood pressure or hypertension" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
med_table$dis_hbp_med_1<-  ifelse(med_table$dis_hbp_med_0==1 | med_table$HBP_EVRMED_COF1=='1',1L, ifelse(med_table$dis_hbp_med_0==0 & med_table$HBP_EVRMED_COF1=='2',0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_hbp_med_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_2  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_3    
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_4  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:   impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_5  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:   impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
# Angina subdomain

### **Variable label**: Lifetime occurrence of angina  
**Variable name**:  dis_angina_ever_0  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of angina (pain or discomfort in chest)" for followup wave was created using "Lifetime occurrence of angina (pain or discomfort in chest)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   

**R script**:  
```{r, echo=TRUE}
med_table$dis_angina_ever_0 <- recode(as.integer(med_table$CCC_ANGI_COM),"1"=1L,"2"=0L, .default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_angina_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_1  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  complete  
**Harmonization comment**:   The harmonized variable "Lifetime occurrence of angina (pain or discomfort in chest)" for followup wave was created using "Lifetime occurrence of angina (pain or discomfort in chest)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   

**R script**:  
```{r, echo=TRUE}
med_table$dis_angina_ever_1<- ifelse(med_table$dis_angina_ever_0==1|         as.integer(med_table$CCC_ANGI_COF1)=='1',1L,ifelse(med_table$dis_angina_ever_0==0&as.integer(med_table$CCC_ANGI_COF1)=='2',0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_angina_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_2  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_3  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_4  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  

# Myocardial infarction subdomain

### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_0  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of myocardial infarction (heart attack)" for followup wave was created using "Lifetime occurrence of myocardial infarction (heart attack)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}
med_table$dis_mi_ever_0 <- recode(as.integer(med_table$CCC_AMI_COM),"1"=1L,"2"=0L,.default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_mi_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_1  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  complete  
**Harmonization comment**: The harmonized variable "Lifetime occurrence of myocardial infarction (heart attack)" for followup wave was created using "Lifetime occurrence of myocardial infarction (heart attack)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   
 
**R script**:  
```{r, echo=TRUE}
table(CLSA_cop_1$CCC_AMI_COF1,useNA='always')
table(med_table$dis_mi_ever_0, med_table$CCC_AMI_COF1,useNA='always')

med_table$dis_mi_ever_1<- ifelse(med_table$dis_mi_ever_0==1 | as.integer(med_table$CCC_AMI_COF1)=='1', 1L, ifelse(med_table$dis_mi_ever_0==0 & as.integer(med_table$CCC_AMI_COF1)=='2',0L, NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_mi_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_2  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_0  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$dis_mi_age_0 <- CLSA_cop_0$IHD_AMIAGE_NB_COM
```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_1  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$dis_mi_age_1<-CLSA_cop_1$IHD_AMIAGE_NB_COF1
```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_2  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
# Stroke subdomain

### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_0  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of stroke or cerebrovascular accident (CVA)" for followup wave was created using "Lifetime occurrence of stroke or cerebrovascular accident (CVA)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   
**R script**:  
```{r, echo=TRUE}
med_table$dis_stroke_ever_0 <- recode(as.integer(med_table$CCC_CVA_COM),"1"=1L,"2"=0L, .default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_stroke_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_1  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  complete  
**Harmonization comment**: The harmonized variable "Lifetime occurrence of stroke or cerebrovascular accident (CVA)" for followup wave was created using "Lifetime occurrence of stroke or cerebrovascular accident (CVA)" from baseline and previous and current wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.   

**R script**:  
```{r, echo=TRUE}
med_table$dis_stroke_ever_1<- ifelse(med_table$dis_stroke_ever_0==1 | med_table$CCC_CVA_COF1=='1',1L, ifelse(med_table$dis_stroke_ever_0==0 & med_table$CCC_CVA_COF1=='2',0L, NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_stroke_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_2  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_0  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$dis_stroke_age_0 <- CLSA_cop_0$STR_CVAAGE_NB_COM
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_1  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$dis_stroke_age_1 <- CLSA_cop_1$STR_CVAAGE_NB_COF1
```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_2  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  


# Diabetes subdomain  

### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar  
**Variable name**: dis_diab_ever_0  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" for followup wave was created using "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" from baseline and followup wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}  
med_table$dis_diab_ever_0 <- recode(as.integer(med_table$DIA_DIAB_COM),"1"=1L,"2"=0L, .default=NA_integer_)
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_0<-merge(oth_CLSA_cop_0,med_table[,c("id","dis_diab_ever_0")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_1  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  complete  
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" for followup wave was created using "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" from baseline and followup wave. To create this variable, all CLSA Comprehensive Cohort data tables were merged by ID in order to facilitate the harmonization work and intermediate variables were created.  
**R script**:  
```{r, echo=TRUE}  
med_table$dis_diab_ever_1<-ifelse(med_table$dis_diab_ever_0==1 | as.integer(med_table$DIA_DIAB_COF1)=='1', 1L, ifelse(med_table$dis_diab_ever_0==0 & as.integer(med_table$DIA_DIAB_COF1)=='2',0L,NA))
#Direct mapping to harmonized tables keeping correct participants for each wave
oth_CLSA_cop_1<-merge(oth_CLSA_cop_1,med_table[,c("id","dis_diab_ever_1")],by="id",all.x=TRUE)
```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_2  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_3  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_4  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_5  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_0    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
oth_CLSA_cop_0$dis_diab_age_0 <- as.integer(CLSA_cop_0$DIA_AGE_NB_COM)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_1    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_2    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_3    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_4    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_5    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}  

```  

### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_0  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  complete  
**Harmonization comment**: The study-specific variable used in harmonization of the DataSchema variable "Currently under treatment for diabetes" is "Are you currently taking medication for diabetes?"  
**R script**:
```{r, echo=TRUE}
oth_CLSA_cop_0$dis_diab_tx_0<-recode(CLSA_cop_0$DIA_MED_COM, '1'=1L,'2'=0L, .default=NA_integer_)
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_1  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_2  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_3  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
 
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_4  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
 
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_5  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_0  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**:  complete  
**Harmonization comment**:  The 7 study-specific variables are asking about the use of six different insulin medications by product names HUMALOG, APIDRA, NOVORAPID, LANTUS, NOVOMIX, LEVEMIR. The combination of whether the participant uses any of these medications and having a valid value in the variable Age began taking insulin are used for the harmonization of this variable. 
**R script**:  
```{r, echo=TRUE}
table(CLSA_cop_0$DIA_MEDAGE_NB_COM, useNA = "always")

#checking whether people who has an age for starting to use insulin use one of these medications. They do. 

CLSA_cop_0$insmed<-NA
CLSA_cop_0$insmed[CLSA_cop_0$DIA_MEDINSNAME_HUMU_COM==0 & CLSA_cop_0$DIA_MEDINSNAME_LEVE_COM==0&CLSA_cop_0$DIA_MEDINSNAME_HUMA_COM==0&CLSA_cop_0$DIA_MEDINSNAME_NOVOR_COM==0&CLSA_cop_0$DIA_MEDINSNAME_NOVOM_COM==0&CLSA_cop_0$DIA_MEDINSNAME_LANT_COM==0]<-0
CLSA_cop_0$insmed[CLSA_cop_0$DIA_MEDINSNAME_HUMU_COM==1|CLSA_cop_0$DIA_MEDINSNAME_LEVE_COM==1|CLSA_cop_0$DIA_MEDINSNAME_HUMA_COM==1|CLSA_cop_0$DIA_MEDINSNAME_NOVOR_COM==1|CLSA_cop_0$DIA_MEDINSNAME_NOVOM_COM==1|CLSA_cop_0$DIA_MEDINSNAME_LANT_COM==1]<-1

table(!is.na(CLSA_cop_0$DIA_MEDAGE_NB_COM),CLSA_cop_0$insmed, useNA = "always")

oth_CLSA_cop_0$dis_diab_ins_0<-ifelse(CLSA_cop_0$insmed==1 |!is.na (CLSA_cop_0$DIA_MEDAGE_NB_COM), 1L, ifelse(CLSA_cop_0$insmed==0 |is.na (CLSA_cop_0$DIA_MEDAGE_NB_COM),0L,NA))

table(oth_CLSA_cop_0$dis_diab_ins_0,useNA = "always" )
```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_1  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_2  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**:  impossible  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
# BMI subdomain

### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_0  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete    
**Harmonization comment**:   There are three study-specific variables: Measurement 1, Measurement 2, and Average. Average of the Measurement 1 and Measurement 2 is used to harmonize.  
**R script**:  
```{r, echo=TRUE}
#There are more NAs in the average weight variable, maybe we should take 1st or
summary(CLSA_cop_0$WGT_WEIGHT1_KG_COM)
summary(CLSA_cop_0$WGT_WEIGHT2_KG_COM)
summary(CLSA_cop_0$WGT_WEIGHT_KG_COM)
table(is.na(CLSA_cop_0$WGT_WEIGHT1_KG_COM), is.na(CLSA_cop_0$WGT_WEIGHT2_KG_COM))
table(CLSA_cop_0$WGT_WEIGHT2_KG_COM[is.na(CLSA_cop_0$WGT_WEIGHT_KG_COM)])
table(CLSA_cop_0$WGT_WEIGHT1_KG_COM[is.na(CLSA_cop_0$WGT_WEIGHT_KG_COM)])
av<-(CLSA_cop_0$WGT_WEIGHT1_KG_COM+ CLSA_cop_0$WGT_WEIGHT2_KG_COM)/2
cor(av, as.numeric(CLSA_cop_0$WGT_WEIGHT_KG_COM), use = "complete.obs")

oth_CLSA_cop_0$phy_weight_ms_0<-(CLSA_cop_0$WGT_WEIGHT1_KG_COM+ CLSA_cop_0$WGT_WEIGHT2_KG_COM)/2
summary(oth_CLSA_cop_0$phy_weight_ms_0)
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_1  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   There are three study-specific variables: Measurement 1, Measurement 2, and Average. Average of the Measurement 1 and Measurement 2 is used to harmonize. 
**R script**:  
```{r, echo=TRUE}
summary(CLSA_cop_1$WGT_WEIGHT_KG_COF1)
summary(CLSA_cop_1$WGT_WEIGHT1_KG_COF1)
summary(CLSA_cop_1$WGT_WEIGHT2_KG_COF1)

oth_CLSA_cop_1$phy_weight_ms_1<-CLSA_cop_1$WGT_WEIGHT_KG_COF1
summary(oth_CLSA_cop_1$phy_weight_ms_1)
```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_2  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_3  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_4  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_5  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_6  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_0    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_1    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
summary(CLSA_cop_1$WGT_WEIGHTSR_KG_COF1)
oth_CLSA_cop_1$phy_weight_sr_1 <-as.numeric(CLSA_cop_1$WGT_WEIGHTSR_KG_COF1)

summary(oth_CLSA_cop_1$phy_weight_sr_1)

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_2    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_3    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_4    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_5    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_6    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_0      
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**: The CLSA Comprehensive Cohort datasets includes Weight Measurement 1, Weight Measurement 2 and the Average Weight from these two measurements. In creation of the DataSchema variable, the Average Weight is used. 
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_weight_all_0<-as.numeric(CLSA_cop_0$WGT_WEIGHT_KG_COM)
summary(oth_CLSA_cop_0$phy_weight_all_0)
table(oth_CLSA_cop_0$phy_weight_all_0[oth_CLSA_cop_0$phy_weight_all_0>130])
```  

### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_1    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:  The CLSA Comprehensive Cohort datasets  includes Weight Measurement 1, Weight Measurement 2 and the Average Weight from these two measurements. In creation of the DataSchema variable, the Average Weight is used. 
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_weight_all_1<-as.numeric(CLSA_cop_1$WGT_WEIGHT_KG_COF1)
summary(oth_CLSA_cop_1$phy_weight_all_1)

```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_2    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_3     
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal   
**Variable unit**: kg    
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_4    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_5    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_6    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_0  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:  The study specific variables include Measurement 1 -height in cm, Measurement 2-height in cm, and Average height in m. The variable Average Height is used for harmonizing this variable.   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_height_ms_0<-CLSA_cop_0$HGT_HEIGHT_M_COM*100
summary(oth_CLSA_cop_0$phy_height_ms_0)
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_1  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:    The study specific variables include Measurement 1 -height in cm, Measurement 2-height in cm, and Average height in m. The variable Average Height is used for harmonizing this variable.  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_height_ms_1<-CLSA_cop_1$HGT_HEIGHT_M_COF1*100
summary(oth_CLSA_cop_1$phy_height_ms_1)
```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_2  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_3  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm    
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_4  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_5  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_6  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_0  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_1  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_height_sr_1<- ifelse(CLSA_cop_1$HGT_HEIGHTSR_CM_COF1==-99999.00, NA, CLSA_cop_1$HGT_HEIGHTSR_CM_COF1 ) 
summary(oth_CLSA_cop_1$phy_height_sr_1, useNA="always")
```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_2  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_3  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_4  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_5  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_6  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_0    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(CLSA_cop_0$HGT_HEIGHT_M_COM)
oth_CLSA_cop_0$phy_height_all_0<-CLSA_cop_0$HGT_HEIGHT_M_COM*100
summary(oth_CLSA_cop_0$phy_height_all_0, useNA = "always")
```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_1    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_height_all_1<-CLSA_cop_1$HGT_HEIGHT_M_COF1*100
summary(oth_CLSA_cop_1$phy_height_all_1, useNA="always")
table(is.na(oth_CLSA_cop_0$phy_height_all_0)) 
```  
### **Variable label**: Height in cm - measured and self-reported combined    
**Variable name**: phy_height_all_2    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_3    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_4    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_5    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_6    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_bmi_ms_0 <-CLSA_cop_0$HWT_DBMI_COM




```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:   complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_bmi_ms_1 <-CLSA_cop_1$HWT_DBMI_COF1
summary(oth_CLSA_cop_1$phy_bmi_ms_1)

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible     
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
# oth_CLSA_cop_1$phy_bmi_sr_1<- oth_CLSA_cop_1$phy_height_sr_1 / (oth_CLSA_cop_1$phy_weight_sr_1/100)^2
# summary(oth_CLSA_cop_1$phy_bmi_sr_1)
# summary(CLSA_cop_1$HGT_HEIGHTSR_CM_COF1/(CLSA_cop_1$WGT_WEIGHTSR_KG_COF1)^2)
# table(CLSA_cop_1$HGT_HEIGHTSR_CM_COF1)
# summary(is.na(oth_CLSA_cop_1$phy_height_sr_1))
# table(oth_CLSA_cop_1$phy_weight_sr_1[!is.na(oth_CLSA_cop_1$phy_height_sr_1)])
# table(oth_CLSA_cop_1$phy_bmi_sr_1)
#I get all empty values. participants who have valid values for SR weight doesnt have valid values for SR height and vice
```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_bmi_all_0 <-CLSA_cop_0$HWT_DBMI_COM
summary(oth_CLSA_cop_0$phy_bmi_all_0)
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_bmi_all_1 <-CLSA_cop_1$HWT_DBMI_COF1
summary(oth_CLSA_cop_1$phy_bmi_all_1)
```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_0  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_bmi_cat_ms_0<-recode(as.integer(CLSA_cop_0$HWT_DISW_COM), '1'=0L,'2'=1L, '3'=2L,'4'=3L,'5'=3L,"6"=3L,
                              .default=NA_integer_)
summary(oth_CLSA_cop_0$phy_bmi_cat_ms_0)
table(CLSA_cop_0$HWT_DISW_COM)
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_1  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_bmi_cat_ms_1<-recode(as.integer(CLSA_cop_1$HWT_DISW_COF1), '1'=0L,'2'=1L, '3'=2L,'4'=3L,'5'=3L,"6"=3L,
                              .default=NA_integer_)


summary(oth_CLSA_cop_1$phy_bmi_cat_ms_1)
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_2  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_3  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_4  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_5  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_6  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:   impossible   
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:   impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:   impossible   
**Harmonization comment**:       
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:   impossible   
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$phy_bmi_cat_ms_0<-recode(as.integer(CLSA_cop_0$HWT_DISW_COM), '1'=0L,'2'=1L, '3'=2L,'4'=3L,'5'=3L,"6"=3L,
                              .default=NA_integer_)
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$phy_bmi_cat_ms_1<-recode(as.integer(CLSA_cop_1$HWT_DISW_COF1), '1'=0L,'2'=1L, '3'=2L,'4'=3L,'5'=3L,"6"=3L,
                              .default=NA_integer_)

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Waist circumference in cm - measured and self-reported combined  
**Variable name**: phy_waist_all_0  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:   complete 
**Harmonization comment**:  The waist measurements are taken directly over skin or over 1 or 2 layers of clothing for different participants. The study-specific variable for waist measurement includes the measurements regardless of the clothing layers. 92 percent of the valid waist measurements were done over one layer of clothing. 
**R script**:  
```{r, echo=TRUE}
table(CLSA_cop_0$WHC_WAIST_CM_COM)
27671/(762 +27671+  1426 )

#The measurement 1)on skin, 2)over one layer of clothing, 3)over two layers of clothing
table(CLSA_cop_0$WHC_CLTHLAYERS_COM)
oth_CLSA_cop_0$phy_waist_all_0<- as.numeric(CLSA_cop_0$WHC_WAIST_CM_COM)
summary(oth_CLSA_cop_0$phy_waist_all_0)

```  

### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_1  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#table(CLSA_cop_1$WHC_WAIST_CM_COF1)
#the variable WHC_WAIST_CM_COF1 exists but there is only one non-missing value
```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_2  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_3  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.     
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_4  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_5  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_6  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  


# General perception of health subdomain

### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_0  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: complete   
**Harmonization comment**:   Study specific variable for self-rated health have 5 categories: Excellent, Very Good, Good, Fair and Poor. Excellent, Very Good and Good are coded as Good health.  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$poh_sah_0 <- recode(CLSA_cop_0$GEN_HLTH_COM,'1'=0L,'2'=0L, '3'=0L,'4'=1L,'5'=2L, .default=NA_integer_)
```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_1  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: complete   
**Harmonization comment**:   Study specific variable for self-rated health have 5 categories: Excellent, Very Good, Good, Fair and Poor. Excellent, Very Good and Good are coded as Good health.  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$poh_sah_1<- recode(CLSA_cop_1$GEN_HLTH_COF1,'1'=0L,'2'=0L, '3'=0L,'4'=1L,'5'=2L,.default=NA_integer_)
```   
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_2  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_3  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_4  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_5  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_6  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_0  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$poh_sah_poor_0 <- recode(as.integer(CLSA_cop_0$GEN_HLTH_COM),'5'=0L,'4'=1L,'1'=1L,'2'=1L,'3'=1L, .default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$poh_sah_poor_1<- recode(as.integer(CLSA_cop_1$GEN_HLTH_COF1),'5'=0L,'4'=1L,'1'=1L,'2'=1L,'3'=1L,.default=NA_integer_)
```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_2  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_3  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_5  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_6  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_0    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$poh_sah_good_0<- recode(as.integer(CLSA_cop_0$GEN_HLTH_COM),'4'=0L,'5'=0L,'1'=1L,'2'=1L,'3'=1L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$poh_sah_good_1<- recode(as.integer(CLSA_cop_1$GEN_HLTH_COF1),'4'=0L,'5'=0L,'1'=1L,'2'=1L,'3'=1L,.default=NA_integer_)
```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_2    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_3    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_5    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_6    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  


# Disability subdomain

### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_0   
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variables is categorized as Yes | No | unable to do | Don't do on doctor's orders. "Don't do on doctor's orders" is coded to "Has difficulty walking up and down the stairs".  
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$fct_stairs_diff_0 <- recode(as.integer(CLSA_cop_0$FUL_FSTR_COM),'2'=0L,'1'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variables is categorized as Yes | No | unable to do | Don't do on doctor's orders. "Don't do on doctor's orders" is coded to "Has difficulty walking up and down the stairs".    
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$fct_stairs_diff_1 <- recode(as.integer(CLSA_cop_1$FUL_FSTR_COF1),'2'=0L,'1'=1L,'3'=1L,'4'=1L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_0  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:   Study-specific variables is categorized as Yes | No | unable to do | Don't do on doctor's orders. "Don't do on doctor's orders" is coded to "Has difficulty walking up and down the stairs".     
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_0$fct_walk_diff_0 <- recode(as.integer(CLSA_cop_0$FUL_WK23B_COM),'2'=1L,'1'=0L,'3'=0L,'4'=0L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  complete  
**Harmonization comment**:  Study-specific variables is categorized as Yes | No | unable to do | Don't do on doctor's orders. "Don't do on doctor's orders" is coded to "Has difficulty walking up and down the stairs".      
**R script**:  
```{r, echo=TRUE}
oth_CLSA_cop_1$fct_walk_diff_1 <-recode(as.integer(CLSA_cop_1$FUL_WK23B_COF1),'2'=1L,'1'=0L,'3'=0L,'4'=0L,.default=NA_integer_)
```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_3  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_4  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_5  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_6  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  



