---
title: "Other outcomes DataSchema"
output: html_document
---
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [BMI subdomain](#bmi-subdomain)
6. [General perception of health subdomain](#general-perception-of-health-subdomain)
7. [Disability subdomain](#disability-subdomain)
8. [Medication use subdomain](#medication-use-subdomain)
9. [LUCAS functional ability index subdomain](#lucas-functional-ability-index-subdomain)

# Hypertension subdomain

### **Variable label**:   
**Variable name**:   
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**:   
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Angina subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Myocardial infarction subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Stroke subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# BMI subdomain

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_0  
**Variable description**: Weight of participant in kilograms at baseline  
**Value type**: integer  
**Variable unit**: kilogram   
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg 
**Variable name**: OTH_WEIGHT_1  
**Variable description**: Weight of participant in kilograms at first follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_2  
**Variable description**: Weight of participant in kilograms at second follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_3  
**Variable description**: Weight of participant in kilograms at third follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_4  
**Variable description**: Weight of participant in kilograms at fourth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_5  
**Variable description**: Weight of participant in kilograms at fifth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_6  
**Variable description**: Weight of participant in kilograms at sixth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_0  
**Variable description**: Height of participant in centimeters at baseline  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_1  
**Variable description**: Height of participant in centimeters at first follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_2  
**Variable description**: Height of participant in centimeters at second follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_3  
**Variable description**: Height of participant in centimeters at third follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_4  
**Variable description**: Height of participant in centimeters at fourth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_5  
**Variable description**: Height of participant in centimeters at fifth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_6  
**Variable description**: Height of participant in centimeters at sixth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_0  
**Variable description**: Body mass index at baseline  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_1  
**Variable description**: Body mass index at first follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_2  
**Variable description**: Body mass index at second follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_3  
**Variable description**: Body mass index at third follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_4  
**Variable description**: Body mass index at fourth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_5  
**Variable description**: Body mass index at fifth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_6  
**Variable description**: Body mass index at sixth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Body mass index status???  
**Variable name**: OTH_BMI_STAT_0  
**Variable description**: Body mass index status at baseline  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-25  
2 | Overweight - BMI 25-30  
3 | Obese - BMI >30  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# General perception of health subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Disability subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Medication use subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# LUCAS functional ability index subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

