---
title: "Other outcomes DataSchema"
output: html_document
---
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [BMI subdomain](#bmi-subdomain)
6. [General perception of health subdomain](#general-perception-of-health-subdomain)
7. [Disability subdomain](#disability-subdomain)
8. [Medication use subdomain](#medication-use-subdomain)
9. [LUCAS functional ability index subdomain](#lucas-functional-ability-index-subdomain)

# Hypertension subdomain

### **Variable label**: High blood pressure or hypertension status  
**Variable name**: oth_hbp_ever  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during participant’s lifetime   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: High blood pressure medication  
**Variable name**:  oth_hbp_med  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Angina subdomain

### **Variable label**: Angina status  
**Variable name**:  oth_angina_ever  
**Variable description**:  Occurrence of angina (chest pain or discomfort caused by a lack of oxygen-rich blood reaching the heart) at any point during participant's lifetime  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Myocardial infarction subdomain

### **Variable label**: Myocardial infarction status  
**Variable name**:  oth_mi_ever  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during participant's lifetime  
**Value type**:  N/A  
**Variable unit**:  integer  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never experienced myocardial infarction
1        |   Ever experienced myocardial infarction  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Myocardial infarction: age at first diagnosis  
**Variable name**:  oth_mi_age  
**Variable description**:  Age at first diagnosis of myocardial infarction  
**Value type**:  integer  
**Variable unit**:  Age in years
**Category coding**: N/A 
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Stroke subdomain

### **Variable label**: Stroke status  
**Variable name**:  oth_stroke_ever  
**Variable description**:  Occurrence of stroke or cerebrovascular incident at any point during participant's lifetime  
**Value type**:  N/A  
**Variable unit**:  integer  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or cerebrovascular incident
1        |   Ever had stroke or cerebrovascular incident  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Diabetes subdomain  

### **Variable label**: Diabetes status  
**Variable name**: oth_diab_ever  
**Variable description**:  Occurrence of diabetes at any point during participant’s lifetime  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Diabetes: age at first diagnosis  
**Variable name**:  oth_diab_age  
**Variable description**: Age at first diagnosis of diabetes  
**Value type**:  integer  
**Variable unit**:  Age in years 
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Diabetes treatment  
**Variable name**:  oth_diab_trt  
**Variable description**:  Indicator of whether participant has ever received medical treatment for diabetes  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Never received treatment for diabetes  
1        | Ever received treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Diabetes insulin use  
**Variable name**:  oth_diab_ins  
**Variable description**:  Indicator of whether participant has ever used insulin for diabetes treatment  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Never has used insulin for diabetes treatment  
1        | Ever has used insulin for diabetes treatment  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# BMI subdomain

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_0  
**Variable description**: Weight of participant in kilograms at baseline  
**Value type**: integer  
**Variable unit**: kilogram   
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg 
**Variable name**: OTH_WEIGHT_1  
**Variable description**: Weight of participant in kilograms at first follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_2  
**Variable description**: Weight of participant in kilograms at second follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_3  
**Variable description**: Weight of participant in kilograms at third follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_4  
**Variable description**: Weight of participant in kilograms at fourth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_5  
**Variable description**: Weight of participant in kilograms at fifth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg  
**Variable name**: OTH_WEIGHT_6  
**Variable description**: Weight of participant in kilograms at sixth follow-up  
**Value type**: integer  
**Variable unit**: kilogram  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_0  
**Variable description**: Height of participant in centimeters at baseline  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_1  
**Variable description**: Height of participant in centimeters at first follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_2  
**Variable description**: Height of participant in centimeters at second follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_3  
**Variable description**: Height of participant in centimeters at third follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_4  
**Variable description**: Height of participant in centimeters at fourth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_5  
**Variable description**: Height of participant in centimeters at fifth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters  
**Variable name**: OTH_HEIGHT_6  
**Variable description**: Height of participant in centimeters at sixth follow-up  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_0  
**Variable description**: Body mass index at baseline  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_1  
**Variable description**: Body mass index at first follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_2  
**Variable description**: Body mass index at second follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_3  
**Variable description**: Body mass index at third follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_4  
**Variable description**: Body mass index at fourth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_5  
**Variable description**: Body mass index at fifth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI)  
**Variable name**: OTH_BMI_6  
**Variable description**: Body mass index at sixth follow-up  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Body mass index status???  
**Variable name**: OTH_BMI_STAT_0  
**Variable description**: Body mass index status at baseline  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-25  
2 | Overweight - BMI 25-30  
3 | Obese - BMI >30  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# General perception of health subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Disability subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Medication use subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# LUCAS functional ability index subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

