---
title: "Other outcomes DataSchema"
output: html_document
---
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [BMI subdomain](#bmi-subdomain)
6. [General perception of health subdomain](#general-perception-of-health-subdomain)
7. [Disability subdomain](#disability-subdomain)

# Hypertension subdomain

### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: DIS_HBP_EVER_0  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: DIS_HBP_EVER_1  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  DIS_HBP_MED_0  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Medication for high blood pressure or hypertension  
**Variable name**:  DIS_HBP_MED_1  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  DIS_HBP_MED_2  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  DIS_HBP_MED_3    
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  DIS_HBP_MED_4  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  DIS_HBP_MED_5  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Angina subdomain

### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  DIS_ANGINA_EVER_0  
**Variable description**:  Occurrence of angina (pain or discomfort in chest caused by a lack of oxygen-rich blood reaching the heart) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  DIS_ANGINA_EVER_1  
**Variable description**:  Occurrence of angina (pain or discomfort in chest caused by a lack of oxygen-rich blood reaching the heart) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  DIS_ANGINA_EVER_2  
**Variable description**:  Occurrence of angina (pain or discomfort in chest caused by a lack of oxygen-rich blood reaching the heart) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  DIS_ANGINA_EVER_3  
**Variable description**:  Occurrence of angina (pain or discomfort in chest caused by a lack of oxygen-rich blood reaching the heart) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  DIS_ANGINA_EVER_4  
**Variable description**:  Occurrence of angina (pain or discomfort in chest caused by a lack of oxygen-rich blood reaching the heart) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

# Myocardial infarction subdomain

### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  DIS_MI_EVER_0  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  DIS_MI_EVER_1  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  DIS_MI_EVER_2  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  DIS_MI_AGE_0  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  DIS_MI_AGE_1  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  DIS_MI_AGE_2  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Stroke subdomain

### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  DIS_STROKE_EVER_0  
**Variable description**:  Occurrence of stroke or cerebrovascular incident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  DIS_STROKE_EVER_1  
**Variable description**:  Occurrence of stroke or cerebrovascular incident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  DIS_STROKE_EVER_2  
**Variable description**:  Occurrence of stroke or cerebrovascular incident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  DIS_STROKE_AGE_0  
**Variable description**:  Age of the participant at time of first stroke.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  DIS_STROKE_AGE_1  
**Variable description**:  Age of the participant at time of first stroke.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  DIS_STROKE_AGE_2  
**Variable description**:  Age of the participant at time of first stroke.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  


# Diabetes subdomain  

### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar  
**Variable name**: DIS_DIAB_EVER_0  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: DIS_DIAB_EVER_1  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: DIS_DIAB_EVER_2  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: DIS_DIAB_EVER_3  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: DIS_DIAB_EVER_4  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes or high blood sugar     
**Variable name**: DIS_DIAB_EVER_5  
**Variable description**:  Occurrence of diabetes, borderline diabetes or high blood sugar at any point during the life of the. participant    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_0    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_1    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_2    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_3    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_4    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes or high blood sugar  
**Variable name**:  DIS_DIAB_AGE_5    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  Age in years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_0  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_1  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_2  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_3  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_4  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  DIS_DIAB_TX_5  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  DIS_DIAB_INS_0  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  DIS_DIAB_INS_1  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  DIS_DIAB_INS_2  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently has used insulin for diabetes treatment  

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# BMI subdomain

### **Variable label**: Weight in kg - measured 
**Variable name**: OTH_WEIGHT_MS  
**Variable description**: Weight of participant in kilograms - measured.  
**Value type**: integer  
**Variable unit**: kilogram   
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg - self-reported 
**Variable name**: OTH_WEIGHT_SR    
**Variable description**: Weight of participant in kilograms - self-reported.  
**Value type**: integer  
**Variable unit**: kilogram   
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Weight in kg - self-reported and measured combined
**Variable name**: OTH_WEIGHT_ALL    
**Variable description**: Weight of participant in kilograms - self-reported  and measured combined.
**Value type**: integer  
**Variable unit**: kilogram   
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters - measured  
**Variable name**: OTH_HEIGHT_MS  
**Variable description**: Height of participant in centimeters - measured.  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters - self-reported  
**Variable name**: OTH_HEIGHT_SR  
**Variable description**: Height of participant in centimeters - self-reported.  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Height in centimeters - self-reported and measured combined  
**Variable name**: OTH_HEIGHT_ALL  
**Variable description**: Height of participant in centimeters - self-reported and measured combined.  
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: OTH_BMI_MS  
**Variable description**: Body mass index - measured.  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: OTH_BMI_SR  
**Variable description**: Body mass index - self-reported.  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**: Body mass index (BMI) - self-reported and measured combined  
**Variable name**: OTH_BMI_ALL  
**Variable description**: Body mass index - self-reported and measured combined.  
**Value type**: integer  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Body mass index - categories - measured  
**Variable name**: OTH_BMI_CAT_MS  
**Variable description**: Body mass index - categories - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Body mass index - categories - self-reported  
**Variable name**: OTH_BMI_CAT_SR  
**Variable description**: Body mass index - categories - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Body mass index - categories - self-reported and measured combined  
**Variable name**: OTH_BMI_CAT_ALL  
**Variable description**: Body mass index - categories - self-reported and measured combined.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Waist circumference in cm  
**Variable name**: OTH_WAIST  
**Variable description**: Waist circumference in centimeters.    
**Value type**: integer  
**Variable unit**: centimeters  
**Category coding**:  N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# General perception of health subdomain

### **Variable label**:  Self-assessed health  
**Variable name**:  OTH_SAH  
**Variable description**:  Self-assessed health in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Poor self-assessed health  
**Variable name**:  OTH_SAHPOOR  
**Variable description**:  Dichotomous indicator of self-assessed health indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Less than good self-assessed health  
**Variable name**:  OTH_SAHGOOD
**Variable description**:  Dichotomous indicator of self-assessed health indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Disability subdomain

### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  FUN_DIFF_STAIRS_0  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  FUN_DIFF_STAIRS_1  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  FUN_DIFF_STAIRS_2  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**:  Difficulty walking for about 400-500 meters  
**Variable name**:  OTH_DISABLE_WALK  
**Variable description**:  Indicator of whether the participant is able to walk for about 400 to 500 meters. The exact distance may vary slightly between studies.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   not able to walk 400-500 meters  
1 |   able to walk 400-500 meters  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```



