---
title: "Other outcomes DataSchema"
output: html_document
---
```{r, echo=TRUE}
#Load Opal R library
library(opalr)
library(tidyverse)
library(epiDisplay)

# Connecting with Opal data server
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit0','ROTTERDAM.RSII_MINDMAP_13082019_visit0', variables =NULL)

ROTTERDAM_0 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit0') %>% as_tibble %>% arrange(id)


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit1','ROTTERDAM.RSII_MINDMAP_13082019_visit1', variables =NULL)

ROTTERDAM_1 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit1') %>% as_tibble %>% arrange(id)


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit2','ROTTERDAM.RSII_MINDMAP_18102019_visit2', variables =NULL)

ROTTERDAM_2 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit2') %>% as_tibble %>% arrange(id)

opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit3','ROTTERDAM.RSII_MINDMAP_18102019_visit3', variables =NULL)

ROTTERDAM_3 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit3') %>% as_tibble %>% arrange(id)



```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
oth_ROTTERDAM_0 <- data.frame(id = ROTTERDAM_0$id, stringsAsFactors = F) %>% as_tibble %>% arrange(id)
oth_ROTTERDAM_1 <- data.frame(id = ROTTERDAM_1$id, stringsAsFactors = F) %>% as_tibble %>% arrange(id)
oth_ROTTERDAM_2 <- data.frame(id = ROTTERDAM_2$id, stringsAsFactors = F) %>% as_tibble %>% arrange(id)
oth_ROTTERDAM_3 <- data.frame(id = ROTTERDAM_3$id, stringsAsFactors = F) %>% as_tibble %>% arrange(id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal)
```
# Table of Contents
1. [Hypertension subdomain](#hypertension-subdomain)
2. [Angina subdomain](#angina-subdomain)
3. [Myocardial infarction subdomain](#myocardial-infarction-subdomain)
4. [Stroke subdomain](#stroke-subdomain)
5. [Diabetes subdomain](#diabetes-subdomain)
6. [BMI subdomain](#bmi-subdomain)
7. [General perception of health subdomain](#general-perception-of-health-subdomain)
8. [Disability subdomain](#disability-subdomain)

# Hypertension subdomain

### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_0  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**: complete   
**Harmonization comment**: Study-specific variable 'Was a high blood pressure ever measured?' used.   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_0$dis_hbp_ever_0 <- with(ROTTERDAM_0, 
                                       ifelse(ep_pimc8==1, 1L, ifelse(ep_pimc8==0, 0L, NA)))

```  
### **Variable label**: Lifetime occurrence of high blood pressure or hypertension    
**Variable name**: dis_hbp_ever_1  
**Variable description**:  Occurrence of high blood pressure or hypertension at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**  
  
**Code**   | **Category Label**    
-----------| -------------  
0          |  Never had high blood pressure or hypertension  
1          |  Ever had high blood pressure or hypertension  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_0  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension  


**Harmonization status**: complete    
**Harmonization comment**:  The study-specific variable is "Were you ever treated with drugs because of high blood pressure?".  
**R script**:  
```{r, echo=TRUE}
# table(ROTTERDAM_0$ep_pimc8b,useNA="always")
oth_ROTTERDAM_0$dis_hbp_med_0 <- ifelse(ROTTERDAM_0$ep_pimc8b==0, 0L,ifelse(ROTTERDAM_0$ep_pimc8b==1, 1L, NA ))
# oth_ROTTERDAM_0$dis_hbp_med_0 <- with(ROTTERDAM_0, 
#                                       ifelse(ep_pimc8b==0|ep_pimc8b==8, 0L, ifelse(ep_pimc8b==1, 1L, NA )))
# table(oth_ROTTERDAM_0$dis_hbp_med_0,useNA="always")

```  
### **Variable label**: Medication for high blood pressure or hypertension  
**Variable name**:  dis_hbp_med_1  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**: impossible   
**Harmonization comment**:  The study-specific variable is "Are you currently treated with drugs because of high blood pressure?" However, because there are 3-4 years between the waves, and we cannot know if they "ever" were treated with hypertension medication.
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_2  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**: impossible   
**Harmonization comment**:  The study-specific variable is "Are you currently treated with drugs because of high blood pressure?" However, because there are 3-4 years between the waves, and we cannot know if they "ever" were treated with hypertension
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_3    
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure or hypertension  
1        |  Ever taken medication  for high blood pressure or hypertension    


**Harmonization status**: impossible   
**Harmonization comment**:  The study-specific variable is "Are you currently treated with drugs because of high blood pressure?" However, because there are 3-4 years between the waves, and we cannot know if they "ever" were treated with hypertension
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_4  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Medication for high blood pressure or hypertension    
**Variable name**:  dis_hbp_med_5  
**Variable description**:  Indicator of whether the participant has ever taken medication for high blood pressure or hypertension.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**
---------| -----------------------------------------------------
0        |  Never taken medication for high blood pressure
1        |  Ever taken medication  for high blood pressure  


**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```  
# Angina subdomain

### **Variable label**: Lifetime occurrence of angina  
**Variable name**:  dis_angina_ever_0  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**: impossible   
**Harmonization comment**:  Study-specific variable 'Have you had a severe pain across the front of your chest lasting for half an hour or more'.
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_1  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**: impossible   
**Harmonization comment**:  Study-specific variable 'Have you had a severe pain across the front of your chest lasting for half an hour or more since ERGO-s/PLus?'
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_2  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**: impossible   
**Harmonization comment**:  Study-specific variable 'Have you had any pain or discomfort in your chest'
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_3  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Lifetime occurrence of angina 
**Variable name**:  dis_angina_ever_4  
**Variable description**:  Occurrence of angina (pain or discomfort in chest) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
---------|---------------  
0        |  Never had angina
1        |  Ever had angina  
  
**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}


```  

# Myocardial infarction subdomain

### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_0  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**: complete     
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

# table(ROTTERDAM_0$ep_pimc9a, useNA="always")
# table(ROTTERDAM_0$ep_pimc9d, useNA="always")
# table(ROTTERDAM_0$ep_pimc9d,ROTTERDAM_0$ep_pimc9a, useNA="always")

MyMerge <- function(x,y){
  merge(x,y, by= c("id"),all=TRUE)
}

ROTTERDAM_2$startage2 <-ROTTERDAM_2$startage
ROTTERDAM_2$startdat2 <-ROTTERDAM_2$startdat

ROTTERDAM_3$startage3 <-ROTTERDAM_3$startage
ROTTERDAM_3$startdat3 <-ROTTERDAM_3$startdat

med_table <- Reduce(MyMerge, list(ROTTERDAM_0,ROTTERDAM_1,ROTTERDAM_2,ROTTERDAM_3))

# changed second condition (for 1 Ever had myocardial infarction ) to OR statement
med_table$dis_mi_ever_0 <-ifelse(med_table$ep_pimc9d==88 & med_table$ep_pimc9a==88, 0L,
                                       ifelse(med_table$ep_pimc9d<77 | med_table$ep_pimc9a<77,1L, NA))

oth_ROTTERDAM_0<-merge(oth_ROTTERDAM_0,med_table[,c("id","dis_mi_ever_0")],by="id",all.x=TRUE)

# table(oth_ROTTERDAM_0$dis_mi_ever_0, useNA="always")

```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_1  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**: complete     
**Harmonization comment**:  Study-specific variable 'Myocardial infarction after Ergo3-Ergoplus?' and harmonized variable dis_mi_ever_0 used.
**R script**:  
```{r, echo=TRUE}
med_table$dis_mi_ever_1<- ifelse(med_table$e4_dimi==1| med_table$dis_mi_ever_0==1, 1L,
                                 ifelse(med_table$e4_dimi==0 & med_table$dis_mi_ever_0==0, 0L, NA))

oth_ROTTERDAM_1<-merge(oth_ROTTERDAM_1,med_table[,c("id","dis_mi_ever_1")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of myocardial infarction    
**Variable name**:  dis_mi_ever_2  
**Variable description**:  Occurrence of myocardial infarction (heart attack) at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------  
0        |   Never had myocardial infarction
1        |   Ever had myocardial infarction  

**Harmonization status**: complete     
**Harmonization comment**:  Study-specific variable 'Myocardial infarction after ERGO4 and ErgoPlus2 and ErgoJong1' and harmonized variable dis_mi_ever_1 used.
**R script**:  
```{r, echo=TRUE}
med_table$dis_mi_ever_2<- ifelse(med_table$e5_EIMI==1| med_table$dis_mi_ever_1==1, 1L,
                                 ifelse(med_table$e5_EIMI==0& med_table$dis_mi_ever_1==0, 0L, NA))

oth_ROTTERDAM_2<-merge(oth_ROTTERDAM_2,med_table[,c("id","dis_mi_ever_2")],by="id",all.x=TRUE)

```  

### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_0  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: complete    
**Harmonization comment**:  Study-specific variables 'Age at time of first heart attack with admission' and 'Age at time of first heart attack without admission' are dates. Harmonized variable calculated from 'Age at entering the Rotterdam Study' minus years difference between 'Date of entering the Rotterdam Study' and earlier of 'Age at time of first heart attack' variables.
**R script**:  
```{r, echo=TRUE}
# table(ROTTERDAM_0$ep_pimc9b, useNA="always")
# table(ROTTERDAM_0$ep_pimc9e, useNA="always")
# table(ROTTERDAM_0$ep_pimc9b, is.na(ROTTERDAM_0$ep_pimc9e), useNA="always")

med_table$ep_pimc9b_yr <- as.integer(substr(med_table$ep_pimc9b, 1,4))
med_table$ep_pimc9e_yr <- as.integer(substr(med_table$ep_pimc9e, 1,4))
med_table$startdat_yr <- as.integer(substr(med_table$startdat.x, 1,4))

med_table$dis_mi_age_0 <- with(med_table,
                               ifelse(is.na(ep_pimc9b_yr), startage.x - (startdat_yr-ep_pimc9e_yr), 
                                      ifelse(is.na(ep_pimc9e_yr), startage.x - (startdat_yr-ep_pimc9b_yr), 
                                             ifelse(ep_pimc9b_yr < ep_pimc9e_yr, startage.x - (startdat_yr-ep_pimc9b_yr), 
                                                    startage.x - (startdat_yr-ep_pimc9e_yr))))
                                     )
oth_ROTTERDAM_0 <- merge(oth_ROTTERDAM_0, med_table[,c("id","dis_mi_age_0")])

# oth_ROTTERDAM_0$dis_mi_age_0 <-ifelse ((as.integer(substr(ROTTERDAM_0$ep_pimc9b, 1,4)))<(as.integer(substr(ROTTERDAM_0$ep_pimc9e, 1,4))), 
#                              ROTTERDAM_0$startage-((as.integer(substr(ROTTERDAM_0$startdat, 1,4)))-as.integer(substr(ROTTERDAM_0$ep_pimc9b, 1,4))),
#                              ifelse((as.integer(substr(ROTTERDAM_0$ep_pimc9b, 1,4)))>(as.integer(substr(ROTTERDAM_0$ep_pimc9e, 1,4))), 
#                              ROTTERDAM_0$startage-((as.integer(substr(ROTTERDAM_0$startdat, 1,4)))-as.integer(substr(ROTTERDAM_0$ep_pimc9e, 1,4))), NA))

# med_table$dis_mi_age_0 <-ifelse ((as.integer(substr(med_table$ep_pimc9b, 1,4)))<(as.integer(substr(med_table$ep_pimc9e, 1,4))), 
#                              med_table$startage.x-((as.integer(substr(med_table$startdat.x, 1,4)))-as.integer(substr(med_table$ep_pimc9b, 1,4))),
#                              ifelse((as.integer(substr(med_table$ep_pimc9b, 1,4)))>(as.integer(substr(med_table$ep_pimc9e, 1,4))), 
#                              med_table$startage.x-((as.integer(substr(med_table$startdat.x, 1,4)))-as.integer(substr(med_table$ep_pimc9e, 1,4))), NA))

# table(oth_ROTTERDAM_0$dis_mi_age_0, useNA="always")
# table(med_table$dis_mi_age_0, useNA="always")

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_1  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: complete     
**Harmonization comment**: Age at first heart attack reported in the previous wave is combined with the study-specific variable asking about the age at first heart attack since last wave.   
**R script**:  
```{r, echo=TRUE}
# Age at time of first heart attack since Ergo-3/Ergoplus

# table(ROTTERDAM_1$e4_dimif)
# table(!is.na(med_table$dis_mi_age_0), med_table$e4_dimif, useNA = "always")
# with(med_table, table(e4_dimif>startdat.x, useNA="always"))
# med_table[which(med_table$e4_dimif==med_table$startdat.x), c("id","e4_dimif","startdat.x")]
# med_table[which(med_table$e4_dimif<med_table$startdat.x), c("id","e4_dimif","startdat.x")]

med_table$e4_dimif_yr <- as.integer(substr(med_table$e4_dimif, 1,4))
# med_table$fup_visit_1_yr <- as.integer(substr(med_table$fup_visit_1, 1,4))

med_table$dis_mi_age_1 <- with(med_table, 
                                 ifelse(!is.na(dis_mi_age_0), dis_mi_age_0, #startage.x + (e4_dimif_yr-startdat_yr)))
                                        ifelse(e4_dimif>startdat.x, startage.x + (e4_dimif_yr-startdat_yr), NA)))

# med_table$dis_mi_age_1<- ifelse (!is.na(med_table$dis_mi_age_0), med_table$dis_mi_age_0,
#                     ifelse(is.na(med_table$dis_mi_age_0), 
#                            med_table$startage.y-((as.integer(substr(med_table$startdat.y, 1,4)))-as.integer(substr(med_table$e4_dimif, 1,4))),NA))
                         
oth_ROTTERDAM_1<-merge(oth_ROTTERDAM_1,med_table[,c("id","dis_mi_age_1")],by="id",all.x=TRUE)
# table(oth_ROTTERDAM_1$dis_mi_age_1, useNA = "always")
# with(med_table, table(!is.na(dis_mi_age_0), !is.na(dis_mi_age_1), useNA = 'always'))

```  
### **Variable label**: Age at first Myocardial infarction  
**Variable name**:  dis_mi_age_2  
**Variable description**:  Age of the participant at time of first myocardial infarction.  
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: complete    
**Harmonization comment**: Age at first heart attack reported in the previous waves are combined with the study-specific variable asking about the age at first heart attack since last wave. 
**R script**:  
```{r, echo=TRUE}
med_table$dis_mi_age_2 <- with(med_table, 
                                 ifelse(!is.na(dis_mi_age_1), dis_mi_age_1, startage.x + (e5_eimif-startdat_yr)))

# med_table$dis_mi_age_2<- ifelse (!is.na(med_table$dis_mi_age_0), med_table$dis_mi_age_0,
#                          ifelse(is.na(med_table$dis_mi_age_0)&!is.na(med_table$dis_mi_age_1),med_table$dis_mi_age_1,
#                          ifelse(is.na(med_table$dis_mi_age_0)&is.na(med_table$dis_mi_age_1)&!is.na(med_table$e5_eimif), 
#                          med_table$startage2-((as.integer(substr(med_table$startdat2, 1,4)))-as.integer(substr(med_table$e5_eimif, 1,4))),NA)))
                         
oth_ROTTERDAM_2<-merge(oth_ROTTERDAM_2,med_table[,c("id","dis_mi_age_2")],by="id",all.x=TRUE)
# table(oth_ROTTERDAM_2$dis_mi_age_2, useNA = "always")
# with(med_table, table(!is.na(dis_mi_age_1), !is.na(dis_mi_age_2), useNA = 'always'))

```  
# Stroke subdomain

### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_0  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**: complete     
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
med_table$dis_stroke_ever_0<- dplyr::recode(as.integer(ROTTERDAM_0$ep_pimc15), "1"=1L, "0"=0L, .default=NA_integer_)

oth_ROTTERDAM_0<-merge(oth_ROTTERDAM_0,med_table[,c("id","dis_stroke_ever_0")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_1  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Lifetime occurrence of stroke or CVA  
**Variable name**:  dis_stroke_ever_2  
**Variable description**:  Occurrence of stroke or cerebrovascular accident (CVA) at any point during the life of the participant.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  
  
**Code** | **Category Label**  
-------- | -------------  
0        |   Never had stroke or CVA  
1        |   Ever had stroke or CVA  

**Harmonization status**: impossible  
**Harmonization comment**:  There is no stroke related variable in follow-up 1, and the study-specific variable asks about having had a stroke since last interview. 

**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_0  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: complete  
**Harmonization comment**:  Study-specific variable 'At what age was the first time? (stroke)' is in date format. Harmonized variable calculated from 'Age at entering the Rotterdam Study' minus years difference between 'Date of entering the Rotterdam Study' and earlier of 'At what age was the first time? (stroke)'.
**R script**:  
```{r, echo=TRUE}

# table(ROTTERDAM_0$ep_pimc15b, useNA = "always")
# table(ROTTERDAM_0$ep_pimc15b>ROTTERDAM_0$startdat, useNA = "always")

oth_ROTTERDAM_0$dis_stroke_age_0 <- with(ROTTERDAM_0, startage -
                                     (as.integer(substr(ROTTERDAM_0$startdat, 1,4))-as.integer(substr(ROTTERDAM_0$ep_pimc15b, 1,4)))
)
# table(oth_ROTTERDAM_0$dis_stroke_age_0, useNA = 'always')                                   

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_1  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age at first stroke or CVA  
**Variable name**:  dis_stroke_age_2  
**Variable description**:  Age of the participant at time of first stroke or cerebrovascular accident (CVA).      
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A  
         
**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  


# Diabetes subdomain  

### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar  
**Variable name**: dis_diab_ever_0  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: complete 
**Harmonization comment**:  The study-specific question asks: "Do you have diabetes?" Treated as chronic condition, so harmonization status is complete.
**R script**:  
```{r, echo=TRUE}  

med_table$dis_diab_ever_0 <- dplyr::recode(as.integer(med_table$ep_pimc6), "0"=0L, "1"=1L, .default=NA_integer_)

oth_ROTTERDAM_0<-merge(oth_ROTTERDAM_0,med_table[,c("id","dis_diab_ever_0")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_1  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: complete     
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" for followup waves was created using "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" from baseline and previous and current waves.
**R script**:  
```{r, echo=TRUE}  
med_table$dis_diab_ever_1 <- ifelse(med_table$dis_diab_ever_0==1, 1L, 
                             dplyr::recode(as.integer(med_table$e4_didm), "0"=0L, "1"=1L, .default=NA_integer_))

oth_ROTTERDAM_1<-merge(oth_ROTTERDAM_1,med_table[,c("id","dis_diab_ever_1")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_2  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: complete    
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" for followup waves was created using "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" from baseline and previous and current waves.
**R script**:  
```{r, echo=TRUE}  
med_table$dis_diab_ever_2 <- ifelse(med_table$dis_diab_ever_0==1|med_table$dis_diab_ever_1==1, 1L, 
                             dplyr::recode(as.integer(med_table$e5_EIDM), "0"=0L, "1"=1L, .default=NA_integer_))

oth_ROTTERDAM_2<-merge(oth_ROTTERDAM_2,med_table[,c("id","dis_diab_ever_2")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_3  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: complete    
**Harmonization comment**:  The harmonized variable "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" for followup waves was created using "Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar" from baseline and previous and current waves.
**R script**:  
```{r, echo=TRUE}  
med_table$dis_diab_ever_3 <- ifelse(med_table$dis_diab_ever_0==1|med_table$dis_diab_ever_1==1
                                    |med_table$dis_diab_ever_2==1, 1L, 
                             dplyr::recode(as.integer(med_table$e6_EIDM), "0"=0L, "1"=1L, .default=NA_integer_))

oth_ROTTERDAM_3<-merge(oth_ROTTERDAM_3,med_table[,c("id","dis_diab_ever_3")],by="id",all.x=TRUE)

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_4  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Lifetime occurrence of diabetes, borderline diabetes, or high blood sugar     
**Variable name**: dis_diab_ever_5  
**Variable description**:  Occurrence of diabetes, borderline diabetes, or high blood sugar, at any point during the life of the participant.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding:**

**Code**   | **Category Label**
-----------| ---------------------------  
0          |  Never had diabetes  
1          |  Ever had diabetes  

**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_0    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete 
**Harmonization comment**:  Study-specific variable 'Since when do you have diabetes?' is in date format. Harmonized variable calculated from 'Age at entering the Rotterdam Study' minus years difference between 'Date of entering the Rotterdam Study' and earlier of 'Since when do you have diabetes?'.
**R script**:  
```{r, echo=TRUE}  
med_table$ep_pimc6a_yr <- as.integer(substr(med_table$ep_pimc6a, 1,4))
med_table$dis_diab_age_0 <- with(med_table, startage.x-(startdat_yr-ep_pimc6a_yr))

# med_table$dis_diab_age_0 <-ifelse(!is.na(med_table$ep_pimc6a), med_table$startage.x-((as.integer(substr(med_table$startdat.x, 1,4)))-
#                                                                  as.integer(substr(med_table$ep_pimc6a, 1,4))) , NA)
oth_ROTTERDAM_0<-merge(oth_ROTTERDAM_0,med_table[,c("id","dis_diab_age_0")],by="id",all.x=TRUE)
                                   
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_1    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete 
**Harmonization comment**:  Age at first diagnosis reported in the previous waves are combined with the study-specific variable asking about the age at first diagnosis since last wave. 
**R script**:  
```{r, echo=TRUE}  
#??1582-10-04 for   2237 participants  # These are missing or don't know, according to data dictionary
# table(ROTTERDAM_1$e4_didmyr)
# with(med_table, table(e4_didmyr>fup_visit_1))  # 4 participants with e4_didmyr > fup_visit_1
med_table$e4_didmyr_yr <- with(med_table, 
                               ifelse(e4_didmyr!="1582-10-04", as.integer(as.character(substr(e4_didmyr, 1,4))),NA))

med_table$dis_diab_age_1 <- with(med_table,
                                 ifelse(!is.na(dis_diab_age_0), dis_diab_age_0, 
                                        startage.y + (e4_didmyr_yr-startdat_yr)))
with(med_table, table(!is.na(dis_diab_age_0), !is.na(dis_diab_age_1)))

# med_table$dis_diab_age_1 <-ifelse(!is.na(med_table$dis_diab_age_0), med_table$dis_diab_age_0 , 
#                            ifelse(is.na(med_table$dis_diab_age_0) & !is.na(med_table$e4_didmyr)&med_table$e4_didmyr!= "1582-10-04",
#                                   med_table$startage.y-((as.integer(substr(med_table$startdat.y, 1,4)))-
#                                                           as.integer(as.character(substr(med_table$e4_didmyr, 1,4)))) , NA))

oth_ROTTERDAM_1<-merge(oth_ROTTERDAM_1,med_table[,c("id","dis_diab_age_1")],by="id",all.x=TRUE)
# table(oth_ROTTERDAM_1$dis_diab_age_1)
```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_2    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  complete 
**Harmonization comment**:  Age at first diagnosis reported in the previous waves are combined with the study-specific variable asking about the age at first diagnosis since last wave. 
**R script**:  
```{r, echo=TRUE}  
# table(ROTTERDAM_2$e5_EIDMYR)
med_table$e5_EIDMYR_yr <- as.integer(as.character(substr(med_table$e5_EIDMYR, 1,4)))
med_table$dis_diab_age_2 <- with(med_table, 
                                 ifelse(!is.na(dis_diab_age_1), dis_diab_age_1,
                                        ifelse(e5_EIDMYR<7777, startage2+(e5_EIDMYR_yr-startdat_yr), NA)))

# med_table$dis_diab_age_2 <-ifelse(!is.na(med_table$dis_diab_age_0), med_table$dis_diab_age_0 , 
#                            ifelse(!is.na(med_table$dis_diab_age_1), med_table$dis_diab_age_1,
#                            ifelse(is.na(med_table$dis_diab_age_0) &
#                                     is.na(med_table$dis_diab_age_1) &
#                                     !is.na(med_table$e4_didmyr)&med_table$e5_EIDMYR< 7777,
#                                   med_table$startage2-((as.integer(substr(med_table$startdat2, 1,4)))-
#                                                           as.integer(as.character(substr(med_table$e5_EIDMYR, 1,4)))) , NA)))
oth_ROTTERDAM_2<-merge(oth_ROTTERDAM_2,med_table[,c("id","dis_diab_age_2")],by="id",all.x=TRUE)
# table(oth_ROTTERDAM_2$dis_diab_age_2)

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_3    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible
**Harmonization comment**:  Study-specific variable e6_EIDMYR is not in an interpretable format.
**R script**:  
```{r, echo=TRUE}  
# table(ROTTERDAM_3$e6_EIDMYR)
# integer in opal. cant see here???
## TW: 11-digit integer in Opal. Proble with sutdy-specific variable? Check with cohort?

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_4    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  
### **Variable label**: Age at diagnosis of diabetes, borderline diabetes, or high blood sugar  
**Variable name**:  dis_diab_age_5    
**Variable description**: Age of the participant at first diagnosis of diabetes, borderline diabetes, or high blood sugar.    
**Value type**:  integer  
**Variable unit**:  years  
**Category coding**: N/A

**Hamonization status**:  
**Harmonization comment**:  impossible 
**R script**:  
```{r, echo=TRUE}  

```  

### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_0  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: complete   
**Harmonization comment**:  The study-specific variable "Is your diabetes treated by injections, tablets or both?" is used for harmonization. If the participant reported being treated by either or both, they are coded under the DataSchema category 1-Currently under treatment for diabetes, whereas if they do not have diabetes or reported not being treated by either method, they are coded under the category 0- Not currently under treatment for diabetes. 
**R script**:
```{r, echo=TRUE}
# table(ROTTERDAM_0$ep_pimc6c, ROTTERDAM_0$ep_pimc6, useNA="always")
oth_ROTTERDAM_0$dis_diab_tx_0 <- ifelse(ROTTERDAM_0$ep_pimc6==0|ROTTERDAM_0$ep_pimc6c==0, 0L,  
                                        ifelse(ROTTERDAM_0$ep_pimc6c==1|ROTTERDAM_0$ep_pimc6c==2|ROTTERDAM_0$ep_pimc6c==3, 1L, NA ))
# table(oth_ROTTERDAM_0$dis_diab_tx_0 )
```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_1  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: complete     
**Harmonization comment**:  The study-specific variable "Is your diabetes treated by injections, tablets or both?" is used for harmonization. If the participant reported being treated by either or both, they are coded under the DataSchema category 1-Currently under treatment for diabetes, whereas if they do not have diabetes or reported not being treated by either method, they are coded under the category 0- Not currently under treatment for diabetes. 
**R script**:
```{r, echo=TRUE}
# table(ROTTERDAM_1$e4_didmtr)
oth_ROTTERDAM_1$dis_diab_tx_1<- ifelse(ROTTERDAM_1$e4_didmtr==0|ROTTERDAM_1$e4_didmtr==8, 0L,  
                                        ifelse(ROTTERDAM_1$e4_didmtr==1|ROTTERDAM_1$e4_didmtr==2|ROTTERDAM_1$e4_didmtr==3, 1L, NA ))
# table(oth_ROTTERDAM_1$dis_diab_tx_1 )

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_2  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: complete     
**Harmonization comment**:  The study-specific variable "Is your diabetes treated by injections, tablets or both?" is used for harmonization. If the participant reported being treated by either or both, they are coded under the DataSchema category 1-Currently under treatment for diabetes, whereas if they do not have diabetes or reported not being treated by either method, they are coded under the category 0- Not currently under treatment for diabetes. 
**R script**:
```{r, echo=TRUE}
# table(ROTTERDAM_2$e5_EIDMTR, ROTTERDAM_2$e5_EIDM)
oth_ROTTERDAM_2$dis_diab_tx_2<- ifelse(ROTTERDAM_2$e5_EIDMTR==0|ROTTERDAM_2$e5_EIDMTR==8, 0L,  
                                        ifelse(ROTTERDAM_2$e5_EIDMTR==1|ROTTERDAM_2$e5_EIDMTR==2|ROTTERDAM_2$e5_EIDMTR==3, 1L, NA ))
# table(oth_ROTTERDAM_2$dis_diab_tx_2)

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_3  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: complete     
**Harmonization comment**:  The study-specific variable "Is your diabetes treated by injections, tablets or both?" is used for harmonziation. If the participant reported being treated by either or both, they are coded under the DataSchema category 1-Currently under treatment for diabetes, whereas if they do not have diabetes or reported not being treated by either method, they are coded under the category 0- Not currently under treatment for diabetes. 
**R script**:
```{r, echo=TRUE}
# table(ROTTERDAM_3$e6_EIDMTR, ROTTERDAM_3$e6_EIDM)
oth_ROTTERDAM_3$dis_diab_tx_3<- ifelse(ROTTERDAM_3$e6_EIDMTR==0|ROTTERDAM_3$e6_EIDMTR==8, 0L,  
                                        ifelse(ROTTERDAM_3$e6_EIDMTR==1|ROTTERDAM_3$e6_EIDMTR==2|ROTTERDAM_3$e6_EIDMTR==3, 1L, NA ))
# table(oth_ROTTERDAM_3$dis_diab_tx_3)

```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_4  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}


```  
### **Variable label**: Currently under treatment for diabetes  
**Variable name**:  dis_diab_tx_5  
**Variable description**:  Indicator of whether the participant is currently under treatment for diabetes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| -------------------------------------  
0        | Not currently under treatment for diabetes  
1        | Currently under treatment for diabetes  

**Harmonization status**: impossible   
**Harmonization comment**:  
**R script**:
```{r, echo=TRUE}


```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_0  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**: impossible  
**Harmonization comment**:  The study-specific variable is :"Is your diabetes treated by injections, tablets or both?"
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_1  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**: impossible  
**Harmonization comment**:  The study-specific variable is :"Is your diabetes treated by injections, tablets or both?"
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Currently use insulin for diabetes  
**Variable name**:  dis_diab_ins_2  
**Variable description**:  Indicator of whether the participant uses insulin for diabetes treatment.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
---------| ---------------------------------------------  
0        | Currently does not use insulin for diabetes treatment  
1        | Currently does use insulin for diabetes treatment  

**Harmonization status**: impossible   
**Harmonization comment**:  The study-specific variable is :"Is your diabetes treated by injections, tablets or both?"
**R script**:  
```{r, echo=TRUE}

```  
# BMI subdomain

### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_0  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_1  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_2  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_3  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_4  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_5  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured 
**Variable name**: phy_weight_ms_6  
**Variable description**: Weight of the participant in kilograms - measured.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_0    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_1    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_2    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_3    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_4    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_5    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported 
**Variable name**: phy_weight_sr_6    
**Variable description**: Weight of the participant in kilograms - self-reported.  
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_0      
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Weight in kg - measured and self-reported combined
**Variable name**: phy_weight_all_1    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$phy_weight_all_1 <-as.numeric(ROTTERDAM_1$e4_230)

```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_2    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: complete     
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$phy_weight_all_2 <-as.numeric(ROTTERDAM_2$e5_230)

```  
### **Variable label**: Weight in kg - measured and self-reported combined  
**Variable name**: phy_weight_all_3     
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal   
**Variable unit**: kg    
**Category coding**: N/A  

**Harmonization status**: complete    
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_3$phy_weight_all_3 <-as.numeric(ROTTERDAM_3$e6_230)

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_4    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_5    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Weight in kg - self-reported and measured combined  
**Variable name**: phy_weight_all_6    
**Variable description**: Weight of the participant in kilograms - measured and self-reported combined. If both measured and self-reported weight were collected, measured weight was taken.   
**Value type**: decimal  
**Variable unit**: kg   
**Category coding**: N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_0  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_1  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_2  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_3  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm    
**Category coding**: N/A

**Harmonization status**: impossible     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
	

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_4  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_5  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured  
**Variable name**: phy_height_ms_6  
**Variable description**: Height of the participant in centimeters - measured.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_0  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_1  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_2  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_3  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_4  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_5  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - self-reported  
**Variable name**: phy_height_sr_6  
**Variable description**: Height of the participant in centimeters - self-reported.  
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_0    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_1    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: complete   
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$phy_height_all_1<- as.numeric(ROTTERDAM_1$e4_229)

```  
### **Variable label**: Height in cm - measured and self-reported combined    
**Variable name**: phy_height_all_2    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: complete    
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$phy_height_all_2<- as.numeric(ROTTERDAM_2$e5_229)

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_3    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: complete    
**Harmonization comment**:   Unknown if study-specific variable is measured or self-reported.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_3$phy_height_all_3 <- as.numeric(ROTTERDAM_3$e6_229)

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_4    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_5    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Height in cm - measured and self-reported combined  
**Variable name**: phy_height_all_6    
**Variable description**: Height of the participant in centimeters - measured  and self-reported combined. If both measured and self-reported height were collected, measured height was taken.   
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible       
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.   
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured  
**Variable name**: phy_bmi_ms_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.  
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - self-reported  
**Variable name**: phy_bmi_sr_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - self-reported.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   

### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_0  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_1  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$phy_bmi_all_1<-as.numeric(ROTTERDAM_1$e4_230)/(as.numeric(ROTTERDAM_1$e4_229)*(0.01))^2

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_2  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$phy_bmi_all_2<-as.numeric(ROTTERDAM_2$e5_230)/(as.numeric(ROTTERDAM_2$e5_229)*(0.01))^2

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_3  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_3$phy_bmi_all_3<-as.numeric(ROTTERDAM_3$e6_230)/(as.numeric(ROTTERDAM_3$e6_229)*(0.01))^2

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_4  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_5  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Body mass index (BMI) - measured and self-reported combined  
**Variable name**: phy_bmi_all_6  
**Variable description**: Weight (in kg) divided by height (in m) squared - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.    
**Value type**: decimal  
**Variable unit**: kg/m2  
**Category coding**: N/A

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_0  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_1  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_2  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_3  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible      
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_4  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_5  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured  
**Variable name**: phy_bmi_cat_ms_6  
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - self-reported  
**Variable name**: phy_bmi_cat_sr_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - self-reported.  
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_0    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_1    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$phy_bmi_cat_all_1 <- ifelse(oth_ROTTERDAM_1$phy_bmi_ms_1<18.5, 0L,
                                     ifelse(oth_ROTTERDAM_1$phy_bmi_ms_1>=18.5&oth_ROTTERDAM_1$phy_bmi_ms_1<25, 1L,
                                     ifelse(oth_ROTTERDAM_1$phy_bmi_ms_1>=25&oth_ROTTERDAM_1$phy_bmi_ms_1<30, 2L, 
                                     ifelse(oth_ROTTERDAM_1$phy_bmi_ms_1>=30, 3L, NA))))

# table(oth_ROTTERDAM_1$phy_bmi_cat_all_1, useNA="always") 
```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_2    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$phy_bmi_cat_all_2 <- ifelse(oth_ROTTERDAM_2$phy_bmi_ms_2<18.5, 0L,
                                    ifelse(oth_ROTTERDAM_2$phy_bmi_ms_2>=18.5 & oth_ROTTERDAM_2$phy_bmi_ms_2<25, 1L,
                                    ifelse(oth_ROTTERDAM_2$phy_bmi_ms_2>=25   & oth_ROTTERDAM_2$phy_bmi_ms_2<30, 2L, 
                                    ifelse(oth_ROTTERDAM_2$phy_bmi_ms_2>=30, 3L, NA))))

# table(oth_ROTTERDAM_2$phy_bmi_cat_all_2, useNA="always")                                      

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_3    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_3$phy_bmi_cat_all_3 <- ifelse(oth_ROTTERDAM_3$phy_bmi_ms_3<18.5, 0L,
                                     ifelse(oth_ROTTERDAM_3$phy_bmi_ms_3>=18.5 & oth_ROTTERDAM_3$phy_bmi_ms_3<25, 1L,
                                     ifelse(oth_ROTTERDAM_3$phy_bmi_ms_3>=25   & oth_ROTTERDAM_3$phy_bmi_ms_3<30, 2L, 
                                     ifelse(oth_ROTTERDAM_3$phy_bmi_ms_3>=30, 3L, NA))))

# table(oth_ROTTERDAM_3$phy_bmi_cat_all_3, useNA="always")                                      

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_4    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_5    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Body mass index (BMI) - categories - measured and self-reported combined  
**Variable name**: phy_bmi_cat_all_6    
**Variable description**: Body mass index in categories - underweight (<18.5 kg/m2), normal (18.5-24.99 kg/m2), overweight (25 to 29.99 kg/m2), obese (30 kg/m2) - measured and self-reported combined. If both measured and self-reported weight and height were collected, measured values were taken.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Underweight - BMI <18.5  
1 | Normal weight - BMI 18.5-24.99  
2 | Overweight - BMI 25-29.99  
3 | Obese - BMI >=30  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**:  Waist circumference in cm - measured and self-reported combined  
**Variable name**: phy_waist_all_0  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_1  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.       
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$phy_waist_all_1<- as.numeric(ROTTERDAM_1$e4_231)

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_2  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$phy_waist_all_2<- as.numeric(ROTTERDAM_2$e5_231)

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_3  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.     
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: complete     
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_3$phy_waist_all_3<- as.numeric(ROTTERDAM_3$e6_231)

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined   
**Variable name**: phy_waist_all_4  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_5  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Waist circumference in cm - measured and self-reported combined 
**Variable name**: phy_waist_all_6  
**Variable description**: Waist circumference of the participant in centimeters - measured and self-reported combined. If both measured and self-reported waist circumference were collected, measured waist circumference was taken.    
**Value type**: decimal  
**Variable unit**: cm  
**Category coding**:  N/A  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# General perception of health subdomain

### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_0  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_1  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_2  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_3  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_4  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_5  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Self-assessed health   
**Variable name**:  poh_sah_6  
**Variable description**:  Self-assessed health of the participant, in three main categories.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Good health  
1 |   Fair health  
2 |   Poor health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  

### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_0  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_2  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_3  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_5  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Poor self-assessed health  
**Variable name**:  poh_sah_poor_6  
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating poor vs non-poor health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Poor health
1 |   Non-poor health

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  

### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_0    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_1    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_2    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_3    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_4    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_5    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Less than good self-assessed health  
**Variable name**:  poh_sah_good_6    
**Variable description**:  Dichotomous indicator of self-assessed health of the participant, indicating good vs less than good health.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Less than good health  
1 |   Good health  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  


# Disability subdomain

### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_0   
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**: complete   
**Harmonization comment**:   The study-specific variable is: "Are you able to climb up and down at least 5 steps of a stair?". 
The categories "with a little effort", "with much effort", not able need help are coded under the DataSchema category 1|Has difficulty walking up and down the stairs; whereas the study-specific category "without effort" is coded under the DataSchema category 0|Has no difficulty walking up and down the stairs.
**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_0$fct_stairs_diff_0<- dplyr::recode(as.integer(ROTTERDAM_0$ep_pishaq11), 
                                                  "1"=0L, "2"=1L, "3"=1L, "4"=1L, .default=NA_integer_)

```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**:  complete     
**Harmonization comment**:   The study-specific variable is: "Are you able to climb up and down at least 5 steps of a stair?". 
The categories "with a little effort", "with much effort", not able need help are coded under the DataSchema category 1|Has difficulty walking up and down the stairs; whereas the study-specific category "without effort" is coded under the DataSchema category 0|Has no difficulty walking up and down the stairs.

**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_1$fct_stairs_diff_1<- dplyr::recode(as.integer(ROTTERDAM_1$e4_di1_11), 
                                                  "1"=0L, "2"=1L, "3"=1L, "4"=1L, .default=NA_integer_)

```  
### **Variable label**:  Difficulty walking up and down the stairs  
**Variable name**:  fct_stairs_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking up and down the stairs.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Has no difficulty walking up and down the stairs
1 |   Has difficulty walking up and down the stairs  

**Harmonization status**: complete     
**Harmonization comment**:   The study-specific variable is: "Are you able to climb up and down at least 5 steps of a stair?". 
The categories "with a little effort", "with much effort", not able need help are coded under the DataSchema category 1|Has difficulty walking up and down the stairs; whereas the study-specific category "without effort" is coded under the DataSchema category 0|Has no difficulty walking up and down the stairs.

**R script**:  
```{r, echo=TRUE}
oth_ROTTERDAM_2$fct_stairs_diff_2<- dplyr::recode(as.integer(ROTTERDAM_2$e5_EI1_11), 
                                                  "1"=0L, "2"=1L, "3"=1L, "4"=1L, .default=NA_integer_)

```  

### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_0  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_1  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_2  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_3  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.   
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_4  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_5  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**:  Difficulty walking    
**Variable name**:  fct_walk_diff_6  
**Variable description**:  Indicator of whether the participant has difficulty walking 2 to 3 blocks, or for about 400 to 500 meters, or for 5 minutes.     
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Not able to walk without difficulty  
1 |   Able to walk without difficulty  

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  



